---
title: "Heterogeneity of Treatment Effects: Reproducibility Script"
subtitle: "All analyses, tables, and figures for the secondary-analysis paper"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    embed-resources: true
    theme: cosmo
    df-print: paged
execute:
  warning: false
  message: false
  echo: true
editor: 
  markdown: 
    wrap: 72
---

## Overview

Public reproducibility script for the secondary-analysis manuscript for HTE analysis with Mexican Healthcare Workers.

The Distress Composite factor scores and the inverse-probability weights are
supplied as columns in the data file rather than refit here as grf's AU-TOC is
sensitive to last-bit changes in its inputs, so the exact values
entered into the published models are provided. The code that generated them is
retained, commented out, in the chunks below.

**To run:** `quarto render` from the folder holding `atme_hte_deid.csv` and the
two SuperLearner helpers. Reference environment: R 4.4.x, grf 2.5.0,
SuperLearner 2.0.29, ranger 0.16.0, glmnet 4.1.8, psych 2.4.6.26, readr
2.1.5 (readr version is important for reproduction) Every forest is fit
with `num.threads = 1` and all seeds are fixed, so the run is deterministic.

------------------------------------------------------------------------

## Setup

```{r setup}
#| echo: false
rm(list = ls(all.names = TRUE))

library(sg)
library(tmle)
library(SuperLearner)
library(glmnet)
library(xgboost)
library(ranger)
library(dplyr)
library(grf)
library(usethis)
library(devtools)
library(tidyverse)
library(quadprog)
library(kernlab)
library(CVXR)
library(cvAUC)
library(doParallel)
library(fastDummies)
library(janitor)
library(psych)
library(GPArotation)

cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# ---- Data load ---------------------------------------------------------------
# The file has no participant identifier, so a stable row-index key is
# synthesized. `id` is never a predictor -- it is an internal join key only.
# Row order in the CSV is the alignment guarantee; do NOT reorder before this.
mydata    <- read.csv("atme_hte_deid.csv", header = TRUE)
mydata$id <- seq_len(nrow(mydata))
full_data <- mydata

# The six supplied vectors must be read with readr (see Overview); base R's
# parser cannot represent some of these doubles.
shipped_cols <- c("distress_factor", "ipw_composite", "ipw_anxiety",
                  "ipw_depression", "ipw_stress", "ipw_wellbeing")
shipped <- readr::read_csv("atme_hte_deid.csv", col_select = all_of(shipped_cols),
                           show_col_types = FALSE)
shipped$id <- seq_len(nrow(shipped))
stopifnot(nrow(shipped) == nrow(mydata))
cat(sprintf("Loaded atme_hte_deid.csv: %d rows x %d columns\n", nrow(mydata), ncol(mydata)))
```

------------------------------------------------------------------------

## Predictor Construction

Identical to all source files (184 baseline predictors: item-level
questionnaire responses + dummy-coded demographics).

```{r predictors}
mydata$intervention_group <- ifelse(mydata$group == "intervention", 1, 0)

t1_num <- mydata %>%
  dplyr::select(starts_with("t1")) %>%
  dplyr::select(where(is.numeric)) %>%
  dplyr::select(
    -tidyselect::matches("(?:^|_)(complete|std_error|cut|clin)(?:$|_)"),
    -tidyselect::matches("(_99$|_no99$)")
  ) %>%
  dplyr::select(-tidyselect::matches("^t1\\.(anx|dep|stress)\\.scale$")) %>%
  mutate(
    t1_training_hours = ifelse(is.na(t1_training_hours), 0, t1_training_hours),
    t1_consulta_ext   = ifelse(t1_consulta_ext == 2, 1, 0)
  )

baseline_vars <- mydata %>%
  select(state, simple_position_english, gender, marital_status, ed_level_reduced, profession)

baseline_vars <- baseline_vars %>%
  mutate(
    gender = case_when(
      is.na(gender) ~ NA_character_,
      tolower(trimws(gender)) %in% c("prefer not to say", "prefiero no decir") ~ NA_character_,
      TRUE ~ as.character(gender)
    )
  )

baseline_vars <- fastDummies::dummy_cols(baseline_vars, select_columns = "gender",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

baseline_vars <- baseline_vars %>%
  mutate(
    simple_position_english = case_when(
      is.na(simple_position_english) | trimws(simple_position_english) == "" ~ "Others",
      TRUE ~ as.character(simple_position_english)
    ),
    simple_position_english = factor(simple_position_english)
  )

baseline_vars <- fastDummies::dummy_cols(baseline_vars,
  select_columns = "simple_position_english",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

baseline_vars <- baseline_vars %>% mutate(state = factor(state))
baseline_vars <- fastDummies::dummy_cols(baseline_vars, select_columns = "state",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

baseline_vars <- baseline_vars %>%
  mutate(
    marital_status = suppressWarnings(as.integer(marital_status)),
    marital_status = factor(marital_status, levels = 1:5,
      labels = c("Single", "Married", "Cohabiting", "Separated", "Widowed"))
  )
baseline_vars <- fastDummies::dummy_cols(baseline_vars, select_columns = "marital_status",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

baseline_vars <- baseline_vars %>%
  mutate(
    ed_level_reduced = suppressWarnings(as.integer(ed_level_reduced)),
    ed_level_reduced = factor(ed_level_reduced, levels = c(2, 3, 4, 5, 6, 7),
      labels = c("Secondary", "Technical career", "Bachelor's degree",
                 "Graduate: specialty", "Graduate: master's", "Graduate: doctorate"))
  )
baseline_vars <- fastDummies::dummy_cols(baseline_vars, select_columns = "ed_level_reduced",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

baseline_vars <- baseline_vars %>%
  mutate(
    profession = factor(profession, levels = 1:15,
      labels = c("Medicine", "Nursing", "Optometry", "Dentistry", "Biomedical sciences",
                 "Psychology", "Health promotion", "Social work", "Chemistry",
                 "Radiology technician", "Laboratory technician", "Physical therapy",
                 "Nutrition", "Public health", "Other")),
    profession = case_when(
      as.character(profession) %in% c("Optometry", "Biomedical sciences", "Health promotion",
                                       "Radiology technician", "Laboratory technician",
                                       "Public health") ~ "Other",
      TRUE ~ as.character(profession)
    ),
    profession = factor(profession, levels = c("Medicine", "Nursing", "Dentistry", "Psychology",
                                               "Social work", "Chemistry", "Physical therapy",
                                               "Nutrition", "Other"))
  )
baseline_vars <- fastDummies::dummy_cols(baseline_vars, select_columns = "profession",
  remove_selected_columns = TRUE, remove_first_dummy = FALSE, ignore_na = TRUE)

add_vars <- c("yrs_work", "household_people", "household_bathroom", "household_rooms",
              "household_internet", "household_cars", "age")
baseline_vars <- baseline_vars %>% bind_cols(mydata %>% select(any_of(add_vars)))

mydata <- bind_cols(
  mydata %>% select(id, intervention_group),
  t1_num,
  baseline_vars
)

mydata <- mydata %>%
  select(-t1_consulta_ext, -gender_female) %>%
  dplyr::select(-any_of(c(
    "t1_anxiety", "t1_depression", "t1_wellbeing", "t1_stress", "t1_maia_selfreg",
    "t1_hm.aware", "t1_hm.connect", "t1_hm.insight", "t1_hm.purpose",
    "t1_ffmq.act", "t1_ffmq.nonr", "t1_cog.emo", "t1_gq6",
    "t1_MBI_NA_emo", "t1_MBI_NA_pa", "t1_emo.ex", "t1_pers.acc",
    "t1_distress", "t1_meaning", "t1_compassion", "t1_iri_ec"
  )))

cat("Predictor columns:", ncol(mydata) - 2, "\n")

skimr::skim(mydata)
```

------------------------------------------------------------------------

## Distress Composite (EFA) and Scree/Parallel Figure

The Distress Composite (`distress_factor`) is a single-factor polychoric EFA on
the 31 follow-up \[t8\] items. The published scores are supplied in the data
file; the scree / Horn parallel-analysis figure for the supplement is built here.

```{r efa-composite}
# 31 follow-up items (auto-detect PROMIS; PSS-10 and WHO-5 constructed directly).
anx_items  <- full_data %>% select(starts_with("t8_promis_edanx")) %>% names()
dep_items  <- full_data %>% select(starts_with("t8_promis_eddep")) %>% names()
pss_items  <- paste0("t8_pss10_", 1:10)
who5_items <- paste0("t8_who5_",  1:5)
all_items  <- c(anx_items, dep_items, pss_items, who5_items)

efa_data <- full_data[, all_items]
n_obs    <- sum(complete.cases(efa_data))

poly_cor <- psych::polychoric(efa_data)

# Horn parallel analysis (seed identical to efa_t8_scales.qmd / v3 draft fig-pa).
set.seed(42)
invisible(capture.output(
  pa_res <- psych::fa.parallel(
    poly_cor$rho, n.obs = n_obs, fa = "fa", fm = "ml", plot = FALSE
  )
))

# Published scores, supplied in the data file. The code that generated them:
#
# efa_1f <- psych::fa(efa_data, nfactors = 1, n.obs = n_obs, cor = "poly", fm = "ml")
# distress_factor_raw <- data.frame(id = full_data$id,
#                                   distress_factor = efa_1f$scores[, 1])
# distress_factor_raw <- distress_factor_raw[!is.na(distress_factor_raw$distress_factor), ]
distress_factor_raw <- shipped %>%
  select(id, distress_factor) %>%
  filter(!is.na(distress_factor)) %>%
  as.data.frame()

cat("  Distress Composite supplied for", nrow(distress_factor_raw), "participants.\n")
```

```{r efa-scree-figure}
# eFigure — scree + Horn parallel analysis (single dominant eigenvalue → 1-factor).
pa_df <- tibble(
  factor    = seq_along(pa_res$fa.values),
  observed  = pa_res$fa.values,
  simulated = pa_res$fa.simr
)

p_efa_scree <- ggplot(pa_df, aes(x = factor)) +
  geom_line(aes(y = observed),  colour = "#01665e", linewidth = 1) +
  geom_point(aes(y = observed), colour = "#01665e", size = 2.3) +
  geom_line(aes(y = simulated), colour = "grey40",  linetype = "dashed", linewidth = 0.7) +
  geom_point(aes(y = simulated), colour = "grey40", size = 1.8, shape = 1) +
  geom_hline(yintercept = 0, colour = "grey70") +
  scale_x_continuous(breaks = seq(1, max(pa_df$factor), by = 2)) +
  labs(x = "Factor", y = "Eigenvalue") +
  theme_minimal(base_size = 10)

print(p_efa_scree)
```

------------------------------------------------------------------------

## Outcomes

All five outcomes are joined once: the four 37-week component scales
plus the Distress Composite. All are excluded from the predictor set, so
`X_all` is identical across the composite and component models.

```{r outcomes}
# distress_factor_raw was built in memory in the EFA chunk above.
stopifnot(
  all(c("id", "distress_factor") %in% names(distress_factor_raw)),
  !any(duplicated(distress_factor_raw$id))
)

mydata <- mydata %>%
  left_join(
    full_data %>% select(id, t8.anx.scale, t8.dep.scale, t8.stress.scale, t8_wellbeing),
    by = "id"
  ) %>%
  left_join(distress_factor_raw %>% select(id, distress_factor), by = "id")

outcome_cols <- c("t8.anx.scale", "t8.dep.scale", "t8.stress.scale",
                  "t8_wellbeing", "distress_factor")

cat("Outcome missingness at t8:\n")
for (col in outcome_cols) {
  cat(sprintf("  %-20s  N missing = %d  (%.1f%%)\n",
              col, sum(is.na(mydata[[col]])), 100 * mean(is.na(mydata[[col]]))))
}
```

------------------------------------------------------------------------

## Median Imputation for Baseline Predictors

```{r impute}
non_pred_cols <- c("id", "intervention_group", outcome_cols)
num_cols      <- names(mydata)[sapply(mydata, is.numeric)]
pred_cols     <- setdiff(num_cols, non_pred_cols)

mydata[pred_cols] <- lapply(mydata[pred_cols], function(v) {
  if (all(is.na(v))) return(v)
  v[is.na(v)] <- median(v, na.rm = TRUE)
  v
})

cat("Predictor NAs after imputation:", sum(sapply(mydata[pred_cols], anyNA)), "\n")
cat("Final predictor count:", length(pred_cols), "\n")
```

------------------------------------------------------------------------

## Predictor Matrix (Full — Built Once)

```{r predictor-matrix}
X_all   <- as.matrix(mydata %>% select(all_of(pred_cols)))
W_all   <- as.integer(mydata$intervention_group)
pid_all <- mydata$id

stopifnot(sum(is.na(X_all)) == 0)
cat("X_all:", nrow(X_all), "rows ×", ncol(X_all), "columns. No missing values.\n")
```

------------------------------------------------------------------------

## SL Library

```{r sl-library}
#| echo: false
# Vendored SuperLearner helpers (ship with this repo; source by relative path).
source("create.Learner.grid.R")
source("SL.ranger.1.R")

screen.lasso.sub <- function(Y, X, family, subs = c(1:ncol(X)), alpha = 1, minscreen = 10,
                             nfolds = 10, nlambda = 100, obsWeights, dfmax = ncol(X) + 1, ...) {
  SuperLearner:::.SL.require('glmnet')
  if (!is.matrix(X)) X <- model.matrix(~ -1 + ., X)
  fitCV <- glmnet::cv.glmnet(x = X, y = Y, lambda = NULL, type.measure = 'default',
                             nfolds = nfolds, weights = obsWeights, dfmax = dfmax,
                             family = family$family, alpha = alpha, nlambda = nlambda, ...)
  whichVariable <- (as.numeric(coef(fitCV$glmnet.fit, s = fitCV$lambda.min))[-1] != 0)
  if (sum(whichVariable) < minscreen) {
    sumCoef       <- apply(as.matrix(fitCV$glmnet.fit$beta), 2, function(x) sum(x != 0))
    newCut        <- which.max(sumCoef >= minscreen)
    whichVariable <- (as.matrix(fitCV$glmnet.fit$beta)[, newCut] != 0)
  }
  return(whichVariable)
}

screen.ranger.sub <- function(Y, X, family, subs = c(1:ncol(X)), nVar = ncol(X),
                              ntree = 1000, mtry = 34, maxdepth = 5,
                              splitrule = ifelse(family$family == 'gaussian', 'variance', 'gini'),
                              obsWeights, ...) {
  SuperLearner:::.SL.require('ranger')
  if (family$family == "gaussian") {
    rank.rf.fit <- ranger::ranger(Y ~ ., data = X, num.trees = ntree, splitrule = splitrule,
                                  max.depth = maxdepth, mtry = ifelse(mtry < ncol(X), mtry, ),
                                  importance = "impurity_corrected", case.weights = obsWeights)
  } else {
    rank.rf.fit <- ranger::ranger(as.factor(Y) ~ ., data = X, num.trees = ntree,
                                  splitrule = splitrule, max.depth = maxdepth,
                                  mtry = ifelse(mtry < ncol(X), mtry, ),
                                  importance = "impurity_corrected", case.weights = obsWeights)
  }
  whichVariable <- as.vector(rank(-rank.rf.fit$variable.importance[1:ncol(X)]) <= nVar)
  return(whichVariable)
}

screen.rare <- function(Y, X, family, thresh = 5, ...) {
  if (family$family == 'binomial') {
    max_limit <- min(table(Y)) - thresh
    min_Y_val <- names(table(Y))[table(Y) == min(table(Y))]
    X_rare    <- X[Y == min_Y_val, ]
  } else {
    max_limit <- nrow(X) - thresh
    X_rare    <- X
  }
  max_freq <- apply(X_rare, 2, function(x) max(table(x)))
  return(max_freq <= max_limit)
}

screen.corr <- function(Y, X, obsWeights, r = 0.95, ...) {
  corr <- cov.wt(X, wt = obsWeights, cor = TRUE)$cor
  if (any(corr[upper.tri(corr, diag = FALSE)] >= r)) {
    high_corr     <- caret::findCorrelation(corr, cutoff = r, names = TRUE)
    whichVariable <- !colnames(X) %in% high_corr
  } else {
    whichVariable <- rep(TRUE, ncol(X))
  }
  return(whichVariable)
}

screen.two_part.lasso <- function(Y, X, thresh = 5, r = 0.95, family, obsWeights,
                                  minscreen = 10, dfmax = ncol(X) + 1, ...) {
  whichNotRare <- screen.rare(Y = Y, X = X, family = family, thresh = thresh, ...)
  X_notRare    <- X[, whichNotRare]
  whichCorr    <- screen.corr(Y = Y, X = X_notRare, r = r, obsWeights = obsWeights, ...)
  screen.x     <- X_notRare[, whichCorr]
  if (length(screen.x) < minscreen) minscreen <- length(screen.x)
  lassoVars    <- screen.lasso.sub(Y = Y, X = screen.x, family = family,
                                   obsWeights = obsWeights, alpha = 1,
                                   minscreen = minscreen, dfmax = dfmax, ...)
  return(colnames(X) %in% colnames(screen.x)[lassoVars])
}

screen.two_part.ranger <- function(Y, X, thresh = 5, r = 0.95, family, obsWeights,
                                   nVar = 30, ...) {
  whichNotRare <- screen.rare(Y = Y, X = X, family = family, thresh = thresh, ...)
  X_notRare    <- X[, whichNotRare]
  whichCorr    <- screen.corr(Y = Y, X = X_notRare, r = r, obsWeights = obsWeights, ...)
  screen.x     <- X_notRare[, whichCorr]
  rangerVars   <- screen.ranger.sub(Y = Y, X = screen.x, family = family,
                                    obsWeights = obsWeights, nVar = nVar, ...)
  return(colnames(X) %in% colnames(screen.x[, rangerVars]))
}

nvar1 <- 25; nvar2 <- 40; nvar3 <- 60

screen.two_part.lasso_1  <- function(...) screen.two_part.lasso(dfmax = nvar1, ...)
screen.two_part.lasso_2  <- function(...) screen.two_part.lasso(dfmax = nvar2, ...)
screen.two_part.lasso_3  <- function(...) screen.two_part.lasso(dfmax = nvar3, ...)
screen.two_part.ranger_1 <- function(...) screen.two_part.ranger(nVar = nvar1, ...)
screen.two_part.ranger_2 <- function(...) screen.two_part.ranger(nVar = nvar2, ...)
screen.two_part.ranger_3 <- function(...) screen.two_part.ranger(nVar = nvar3, ...)

set.seed(250829)
n_tunes      <- 6
n_real_Y     <- 500
tune.glmnet  <- list(alpha = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

tune.grid.ranger1 <- expand.grid(num.trees = 5000L, max.depth = 3:5L,
  min.node.size = as.integer(n_real_Y * c(0.05, 0.1, 0.15)),
  mtry = as.integer(c(max(2, sqrt(nvar1) / 2), sqrt(nvar1), min(nvar1, sqrt(nvar1) * 2))))
tune.grid.ranger2 <- expand.grid(num.trees = 5000L, max.depth = 3:5L,
  min.node.size = as.integer(n_real_Y * c(0.05, 0.1, 0.15)),
  mtry = as.integer(c(max(2, sqrt(nvar2) / 2), sqrt(nvar2), min(nvar2, sqrt(nvar2) * 2))))
tune.grid.ranger3 <- expand.grid(num.trees = 5000L, max.depth = 3:5L,
  min.node.size = as.integer(n_real_Y * c(0.05, 0.1, 0.15)),
  mtry = as.integer(c(max(2, sqrt(nvar3) / 2), sqrt(nvar3), min(nvar3, sqrt(nvar3) * 2))))

selected.tune.ranger1 <- tune.grid.ranger1[sample(nrow(tune.grid.ranger1), n_tunes / 3), ]
selected.tune.ranger2 <- tune.grid.ranger2[sample(nrow(tune.grid.ranger2), n_tunes / 3), ]
selected.tune.ranger3 <- tune.grid.ranger3[sample(nrow(tune.grid.ranger3), n_tunes / 3), ]

grid.glmnet  <- create.Learner("SL.glmnet", tune = tune.glmnet, detailed_names = TRUE)
grid.ranger1 <- create.Learner.grid('SL.ranger.1', detailed_names = TRUE,
                                    tunegrid = selected.tune.ranger1, name_prefix = 'SL.ranger')
grid.ranger2 <- create.Learner.grid('SL.ranger.1', detailed_names = TRUE,
                                    tunegrid = selected.tune.ranger2, name_prefix = 'SL.ranger')
grid.ranger3 <- create.Learner.grid('SL.ranger.1', detailed_names = TRUE,
                                    tunegrid = selected.tune.ranger3, name_prefix = 'SL.ranger')

grid.glmnet.screen  <- lapply(grid.glmnet$names, c,
                               'screen.two_part.lasso_1',
                               'screen.two_part.lasso_2',
                               'screen.two_part.lasso_3')
grid.ranger.screen1 <- lapply(grid.ranger1$names, c, 'screen.two_part.ranger_1')
grid.ranger.screen2 <- lapply(grid.ranger2$names, c, 'screen.two_part.ranger_2')
grid.ranger.screen3 <- lapply(grid.ranger3$names, c, 'screen.two_part.ranger_3')

simple_SL_library <- c(list('SL.mean'), grid.glmnet.screen, grid.ranger.screen1)
cvControl         <- SuperLearner.CV.control(V = 5L, stratifyCV = TRUE)

cat("SL library built. Learner count:", length(simple_SL_library), "\n")
```

------------------------------------------------------------------------

## IPW Weights (per outcome)

Inverse-probability-of-attrition weights: arm-specific SuperLearner missingness
models (seed `12345` per fit). The published weights are supplied in the data
file; the code that produced them is retained below. The composite key
(`distress_factor`) drives all composite-model analyses.

```{r ipw-helper}
# compute_ipw_for_outcome <- function(outcome_col, seed = 12345) {
#   miss_ind <- as.integer(!is.na(mydata[[outcome_col]]))
#
#   int_idx <- mydata$intervention_group == 1
#   y_int   <- miss_ind[int_idx]
#   w_int   <- mydata[int_idx, pred_cols] %>% as.data.frame() %>% janitor::clean_names()
#
#   set.seed(seed)
#   m_int   <- SuperLearner(Y = y_int, X = w_int, family = binomial(),
#                           SL.library = simple_SL_library, cvControl = cvControl, verbose = FALSE)
#   p_int   <- as.numeric(m_int$SL.predict)
#   r_int   <- ifelse(y_int == 1, 1 / p_int, 0)
#   n_int   <- ifelse(y_int == 1, r_int * sum(y_int) / sum(r_int[y_int == 1]), 0)
#
#   ctrl_idx <- mydata$intervention_group == 0
#   y_ctrl   <- miss_ind[ctrl_idx]
#   w_ctrl   <- mydata[ctrl_idx, pred_cols] %>% as.data.frame() %>% janitor::clean_names()
#
#   set.seed(seed)
#   m_ctrl  <- SuperLearner(Y = y_ctrl, X = w_ctrl, family = binomial(),
#                           SL.library = simple_SL_library, cvControl = cvControl, verbose = FALSE)
#   p_ctrl  <- as.numeric(m_ctrl$SL.predict)
#   r_ctrl  <- ifelse(y_ctrl == 1, 1 / p_ctrl, 0)
#   n_ctrl  <- ifelse(y_ctrl == 1, r_ctrl * sum(y_ctrl) / sum(r_ctrl[y_ctrl == 1]), 0)
#
#   ipw <- rep(0, nrow(mydata))
#   ipw[int_idx]  <- n_int
#   ipw[ctrl_idx] <- n_ctrl
#   ipw
# }
```

```{r ipw-load}
ipw_outcome_cols <- list(
  anxiety    = "t8.anx.scale",
  depression = "t8.dep.scale",
  stress     = "t8.stress.scale",
  wellbeing  = "t8_wellbeing",
  composite  = "distress_factor"
)

ipw_weights <- list()

# Supplied weights. Each was produced by:
#   ipw_weights[[key]] <- compute_ipw_for_outcome(ipw_outcome_cols[[key]])
for (key in names(ipw_outcome_cols)) {
  ipw_weights[[key]] <- shipped[[paste0("ipw_", key)]]

  n_comp <- sum(ipw_weights[[key]] > 0, na.rm = TRUE)
  w_comp <- ipw_weights[[key]][ipw_weights[[key]] > 0]
  cat(sprintf("  %-11s N completers with weight > 0: %d  |  weight range: [%.3f, %.3f]\n",
              key, n_comp, min(w_comp), max(w_comp)))
}

# Composite weight vector drives all composite-model analyses.
ipw_composite <- ipw_weights[["composite"]]
stopifnot(length(ipw_composite) == nrow(mydata), !anyNA(ipw_composite))
```

```{r ipw-diagnostics}
# Per-arm response-model discrimination (cross-validated AUC) and normalized-weight
# ranges for the eMethods. Recomputed from scratch (two arm-specific Super Learner
# response models, seed 12345 each).
miss_ind <- as.integer(!is.na(mydata[["distress_factor"]]))

fit_arm_diag <- function(arm_val) {
  idx <- mydata$intervention_group == arm_val
  y   <- miss_ind[idx]
  X   <- mydata[idx, pred_cols] %>% as.data.frame() %>% janitor::clean_names()
  set.seed(12345)
  m   <- SuperLearner(Y = y, X = X, family = binomial(),
                      SL.library = simple_SL_library, cvControl = cvControl,
                      verbose = FALSE)
  cv_pred <- as.numeric(m$Z %*% m$coef)          # out-of-fold ensemble predictions
  folds   <- rep(NA_integer_, length(y))
  for (v in seq_along(m$validRows)) folds[m$validRows[[v]]] <- v
  auc <- cvAUC::ci.cvAUC(predictions = cv_pred, labels = y, folds = folds)
  list(n = length(y), auc = auc$cvAUC, auc_lo = auc$ci[1], auc_hi = auc$ci[2])
}

d_int  <- fit_arm_diag(1)
d_ctrl <- fit_arm_diag(0)

wr <- function(arm_val) {
  w <- ipw_composite[mydata$intervention_group == arm_val]
  w <- w[w > 0]
  c(min = min(w), max = max(w))
}
wr_int  <- wr(1)
wr_ctrl <- wr(0)

ipw_diagnostics <- tibble::tibble(
  arm    = c("Intervention", "Control"),
  n      = c(d_int$n,      d_ctrl$n),
  auc    = c(d_int$auc,    d_ctrl$auc),
  auc_lo = c(d_int$auc_lo, d_ctrl$auc_lo),
  auc_hi = c(d_int$auc_hi, d_ctrl$auc_hi),
  w_min  = c(wr_int["min"], wr_ctrl["min"]),
  w_max  = c(wr_int["max"], wr_ctrl["max"])
)
print(ipw_diagnostics)
```

------------------------------------------------------------------------

## Variable Importance Group Map

```{r group-map}
group_map <- tibble(variable = pred_cols) %>%
  mutate(group = case_when(
    str_starts(variable, "state_")                   ~ "State (dummy)",
    str_starts(variable, "simple_position_english_") ~ "Job position (dummy)",
    str_starts(variable, "marital_status_")          ~ "Marital status (dummy)",
    str_starts(variable, "ed_level_reduced_")        ~ "Education (dummy)",
    str_starts(variable, "profession_")              ~ "Profession (dummy)",
    variable == "gender_male"                        ~ "Gender",
    variable %in% c("yrs_work", "household_people", "household_bathroom",
                    "household_rooms", "household_internet",
                    "household_cars", "age")         ~ "Demographics / SES",
    str_starts(variable, "t1_who5_")                ~ "WHO-5 items (t1)",
    str_starts(variable, "t1_pss10_")               ~ "PSS-10 items (t1)",
    str_starts(variable, "t1_promis_edanx")          ~ "PROMIS Anxiety items (t1)",
    str_starts(variable, "t1_promis_eddep")          ~ "PROMIS Depression items (t1)",
    str_starts(variable, "t1_hmi_")                 ~ "HMI items (t1)",
    str_detect(variable, "^t1_maia[1-9]$")          ~ "MAIA items (t1)",
    str_starts(variable, "t1_fivefacet1_")          ~ "FFMQ Awareness items (t1)",
    str_starts(variable, "t1_fivefacet2_")          ~ "FFMQ Nonreact items (t1)",
    str_starts(variable, "t1_interper_")            ~ "IRI EC items (t1)",
    str_starts(variable, "t1_cogn_emot")            ~ "CERQ Reappraisal items (t1)",
    str_starts(variable, "t1_compassion")           ~ "Compassion items (t1)",
    str_starts(variable, "t1_meaninglife")          ~ "Meaning in Life items (t1)",
    str_starts(variable, "t1_gq6_")                ~ "Gratitude items (t1)",
    str_starts(variable, "t1_globalass")            ~ "Character strengths / GACS-24 items (t1)",
    str_starts(variable, "t1_burnout")              ~ "MBI / Burnout items (t1)",
    variable %in% c("t1_training_socioemo",
                    "t1_training_hours")            ~ "Training / clinical history",
    TRUE                                            ~ "Other / unmapped"
  ))

unmapped <- group_map %>% filter(group == "Other / unmapped")
if (nrow(unmapped) > 0) {
  cat("Unmapped variables (", nrow(unmapped), "):\n"); print(unmapped$variable)
} else {
  cat("All", nrow(group_map), "predictor variables successfully mapped to groups.\n")
}
```

------------------------------------------------------------------------

## `run_hte()` Helper

Single helper (the composite-file superset; returns individual `vi_df`
for top-N selection).

```{r run-hte-fn}
run_hte <- function(outcome_col, label, direction,
                    ipw_vec, mydata, X_mat, W_all, pid_all,
                    p_cols, grp_map,
                    n_trees = 4000) {

  # Seeds identical to original individual analyses:
  #   fold assignment  -> set.seed(12345)
  #   per-fold forest  -> set.seed(123456 + fold), seed = 123456 + fold
  #   eval forest      -> set.seed(1), seed = 1
  #   AUTOC            -> set.seed(12345)

  Y_raw <- mydata[[outcome_col]]
  if (direction == "negate") Y_raw <- Y_raw * -1

  keep <- !is.na(Y_raw) & !is.na(ipw_vec) & ipw_vec > 0

  X   <- X_mat[keep, , drop = FALSE]
  Y   <- as.numeric(scale(Y_raw[keep]))
  W   <- W_all[keep]
  wt  <- as.numeric(ipw_vec[keep])
  pid <- pid_all[keep]
  N   <- sum(keep)

  stopifnot(
    sum(is.na(X))  == 0,
    sum(is.na(Y))  == 0,
    sum(is.na(W))  == 0,
    sum(is.na(wt)) == 0
  )

  cat(sprintf("\n--- %s\n    N = %d  (W=1: %d, W=0: %d)  predictors = %d\n",
              label, N, sum(W == 1), sum(W == 0), ncol(X)))

  # 10-fold cross-fitted CATEs
  K      <- 10
  foldID <- integer(N)
  set.seed(12345)
  for (g in 0:1) {
    idx         <- which(W == g)
    foldID[idx] <- sample(rep(1:K, length.out = length(idx)))
  }

  fold_results <- lapply(1:K, function(fold) {
    train <- which(foldID != fold)
    test  <- which(foldID == fold)
    set.seed(123456 + fold)
    cf <- causal_forest(
      X[train, , drop = FALSE], Y[train], W[train],
      sample.weights = wt[train],
      num.trees      = n_trees,
      seed           = 123456 + fold,
      num.threads    = 1L
    )
    list(row     = test,
         tau_hat = as.numeric(predict(cf, X[test, , drop = FALSE])$predictions))
  })

  tau_oof <- rep(NA_real_, N)
  for (res in fold_results) tau_oof[res$row] <- res$tau_hat
  stopifnot(sum(is.na(tau_oof)) == 0)

  # Evaluation forest
  set.seed(1)
  eval_forest <- causal_forest(X, Y, W,
                               sample.weights = wt,
                               num.trees      = n_trees,
                               seed           = 1,
                               num.threads    = 1L)

  # ATE
  ate_obj <- average_treatment_effect(eval_forest)
  ATE     <- as.numeric(ate_obj["estimate"])
  ATE_SE  <- as.numeric(ate_obj["std.err"])
  cat(sprintf("    ATE: %.4f  (SE = %.4f)\n", ATE, ATE_SE))

  # AUTOC
  set.seed(12345)
  rate_obj <- rank_average_treatment_effect(
    eval_forest,
    priorities = tau_oof,
    target     = "AUTOC",
    q          = seq(0.05, 1, length.out = 100),
    R          = 200
  )
  autoc    <- as.numeric(rate_obj$estimate)
  autoc_se <- as.numeric(rate_obj$std.err)
  ci_lo    <- autoc - 1.96 * autoc_se
  ci_hi    <- autoc + 1.96 * autoc_se
  pval     <- 2 * pnorm(-abs(autoc / autoc_se))
  cat(sprintf("    AUTOC: %.4f  SE: %.4f  95%% CI [%.4f, %.4f]  p = %.4f\n",
              autoc, autoc_se, ci_lo, ci_hi, pval))

  # Quintile ATE plot
  q_breaks <- quantile(tau_oof, probs = seq(0, 1, length.out = 6), na.rm = TRUE)
  grp_q    <- cut(tau_oof, breaks = q_breaks, labels = 1:5, include.lowest = TRUE)

  ate_q <- lapply(1:5, function(g) {
    idx  <- which(grp_q == g)
    vals <- average_treatment_effect(eval_forest, subset = idx)
    data.frame(estimate = as.numeric(vals["estimate"]),
               std.err  = as.numeric(vals["std.err"]))
  })
  df_q <- data.frame(
    do.call(rbind, ate_q),
    group = factor(1:5, labels = paste0("Q", 1:5))
  )

  p_quintile <- ggplot(df_q, aes(x = group, y = estimate)) +
    geom_point(size = 2.5) +
    geom_errorbar(aes(ymin = estimate - 1.96 * std.err,
                      ymax = estimate + 1.96 * std.err), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dotted", colour = "grey50") +
    labs(x     = "CATE quintile",
         y     = "ATE  (positive = intervention benefit)",
         title = paste(label, "— ATE by CATE Quintile")) +
    theme_minimal(base_size = 12)

  # Variable importance — individual level (needed for top-N selection from full model)
  vi_raw <- variable_importance(eval_forest)
  vi_df  <- data.frame(variable   = p_cols,
                       importance = as.numeric(vi_raw)) %>%
    left_join(grp_map %>% select(variable, group), by = "variable") %>%
    mutate(group = tidyr::replace_na(group, "Other / unmapped")) %>%
    arrange(desc(importance))

  vi_grouped <- vi_df %>%
    group_by(group) %>%
    summarise(
      n_items          = n(),
      total_importance = round(sum(importance), 6),
      mean_per_item    = round(mean(importance), 6),
      .groups = "drop"
    ) %>%
    arrange(desc(mean_per_item))

  p_vi <- ggplot(vi_grouped,
                 aes(x = reorder(group, mean_per_item), y = mean_per_item)) +
    geom_col(fill = "steelblue3") +
    coord_flip() +
    labs(x        = NULL,
         y        = "Mean split-frequency importance per item",
         title    = paste(label, "— Variable Importance by Scale"),
         subtitle = "Bars show mean per item; adjusts for scale size") +
    theme_minimal(base_size = 11)

  list(
    label       = label,
    outcome_col = outcome_col,
    N           = N,
    N_treated   = sum(W == 1),
    N_control   = sum(W == 0),
    n_predictors = ncol(X),
    ATE         = ATE,
    ATE_SE      = ATE_SE,
    AUTOC       = autoc,
    AUTOC_SE    = autoc_se,
    CI_lo       = ci_lo,
    CI_hi       = ci_hi,
    p           = pval,
    CATE_SD     = sd(tau_oof),
    rate_obj    = rate_obj,
    p_quintile  = p_quintile,
    vi_df       = vi_df,
    vi_grouped  = vi_grouped,
    p_vi        = p_vi,
    tau_df      = data.frame(id = pid, tau = tau_oof)
  )
}
```

------------------------------------------------------------------------

# Part A — Composite Model (EFA Distress Composite)

## Step 1: Full Model (All Predictors)

```{r run-full}
cat(sprintf("[%s] Fitting full model...\n", format(Sys.time(), "%H:%M:%S")))
res_full <- run_hte(
  outcome_col = "distress_factor",
  label       = "EFA Composite — Full Model",
  direction   = "negate",
  ipw_vec     = ipw_composite,
  mydata      = mydata,
  X_mat       = X_all,
  W_all       = W_all,
  pid_all     = pid_all,
  p_cols      = pred_cols,
  grp_map     = group_map
)
```

## Step 2: Variable Importance Rankings and Top-N Selection

```{r vi-rankings}
vi_all <- res_full$vi_df

cat("Top 30 predictors by individual split-frequency importance:\n\n")
knitr::kable(
  vi_all %>%
    slice_head(n = 30) %>%
    mutate(rank = row_number(), importance = round(importance, 6)) %>%
    select(rank, variable, group, importance),
  caption = "Full model — top 30 predictors by individual split-frequency importance."
)
```

```{r define-top-subsets}
top10_cols <- vi_all$variable[1:10]
top20_cols <- vi_all$variable[1:20]
top30_cols <- vi_all$variable[1:30]

cat("Top-10 predictors:\n");        print(top10_cols)
cat("\nTop-20 (additional):\n");    print(top20_cols[11:20])
cat("\nTop-30 (additional):\n");    print(top30_cols[21:30])
```

## Step 3: Reduced Models (Top 10 / 20 / 30)

```{r run-reduced}
reduced_configs <- list(
  list(key = "top10", label = "EFA Composite — Top 10 Predictors",  cols = top10_cols),
  list(key = "top20", label = "EFA Composite — Top 20 Predictors",  cols = top20_cols),
  list(key = "top30", label = "EFA Composite — Top 30 Predictors",  cols = top30_cols)
)

results_reduced <- list()

for (cfg in reduced_configs) {
  cat(sprintf("[%s] Fitting: %s\n", format(Sys.time(), "%H:%M:%S"), cfg$label))

  X_sub   <- as.matrix(mydata %>% select(all_of(cfg$cols)))
  grp_sub <- group_map %>% filter(variable %in% cfg$cols)

  results_reduced[[cfg$key]] <- run_hte(
    outcome_col = "distress_factor",
    label       = cfg$label,
    direction   = "negate",
    ipw_vec     = ipw_composite,
    mydata      = mydata,
    X_mat       = X_sub,
    W_all       = W_all,
    pid_all     = pid_all,
    p_cols      = cfg$cols,
    grp_map     = grp_sub
  )
}

cat("\nAll reduced composite models complete.\n")
```

## Pipeline Integrity Check

Verifies the composite results against **the values published in the
manuscript**, taken verbatim from the internal analysis file. This is a real
check, not a self-consistency check: the script recomputes every forest from
the raw data and must land on the paper's numbers. Any drift halts the render.

Matching exactly depends on the precision-path round-trips documented in the
EFA and IPW chunks. Remove them and the AU-TOC estimates move by ~0.005 — small
relative to their standard errors (~0.05), but enough to change which reduced
specification ranks highest.

```{r pipeline-check}
# Published manuscript values, verbatim. Expected to reproduce exactly.
expected <- list(
  full  = list(N = 1435L, N_treated = 680L, N_control = 755L,
               n_predictors = 184L,
               ATE = 0.3289, ATE_SE = 0.0472,
               AUTOC = 0.1551, AUTOC_SE = 0.0608, p = 0.0107),
  top10 = list(N = 1435L, N_treated = 680L, N_control = 755L,
               n_predictors = 10L,
               ATE = 0.3190, ATE_SE = 0.0483,
               AUTOC = 0.2020, AUTOC_SE = 0.0513, p = 0.0001),
  top20 = list(N = 1435L, N_treated = 680L, N_control = 755L,
               n_predictors = 20L,
               ATE = 0.3376, ATE_SE = 0.0470,
               AUTOC = 0.2064, AUTOC_SE = 0.0508, p = 0.00005),
  top30 = list(N = 1435L, N_treated = 680L, N_control = 755L,
               n_predictors = 30L,
               ATE = 0.3373, ATE_SE = 0.0468,
               AUTOC = 0.1937, AUTOC_SE = 0.0518, p = 0.0002)
)

tol_small <- 0.0002
tol_se    <- 0.001

check_model <- function(key, res, exp) {
  ok <- TRUE
  flags <- character(0)

  check <- function(label, actual, target, tol) {
    if (abs(actual - target) > tol) {
      flags <<- c(flags, sprintf("  %s: got %.4f, expected %.4f (diff %.4f)",
                                 label, actual, target, abs(actual - target)))
      ok <<- FALSE
    }
  }

  if (res$N          != exp$N)           { flags <- c(flags, sprintf("  N: got %d, expected %d", res$N, exp$N)); ok <- FALSE }
  if (res$N_treated  != exp$N_treated)   { flags <- c(flags, sprintf("  N_treated: got %d, expected %d", res$N_treated, exp$N_treated)); ok <- FALSE }
  if (res$N_control  != exp$N_control)   { flags <- c(flags, sprintf("  N_control: got %d, expected %d", res$N_control, exp$N_control)); ok <- FALSE }
  if (res$n_predictors != exp$n_predictors) { flags <- c(flags, sprintf("  n_predictors: got %d, expected %d", res$n_predictors, exp$n_predictors)); ok <- FALSE }

  check("ATE",      res$ATE,      exp$ATE,      tol_small)
  check("ATE_SE",   res$ATE_SE,   exp$ATE_SE,   tol_se)
  check("AUTOC",    res$AUTOC,    exp$AUTOC,     tol_small)
  check("AUTOC_SE", res$AUTOC_SE, exp$AUTOC_SE,  tol_se)

  if ((res$p < 0.05) != (exp$p < 0.05)) {
    flags <- c(flags, sprintf("  p-value significance changed: got %.4f, expected %.4f", res$p, exp$p))
    ok <- FALSE
  }

  tau <- res$tau_df$tau
  if (any(is.na(tau))) { flags <- c(flags, sprintf("  tau_df has %d NAs", sum(is.na(tau)))); ok <- FALSE }
  if (nrow(res$tau_df) != exp$N) { flags <- c(flags, sprintf("  tau_df nrow: got %d, expected %d", nrow(res$tau_df), exp$N)); ok <- FALSE }
  missing_ids <- setdiff(res$tau_df$id, full_data$id)
  if (length(missing_ids) > 0) { flags <- c(flags, sprintf("  %d IDs in tau_df not found in full_data", length(missing_ids))); ok <- FALSE }

  if (ok) {
    cat(sprintf("PASS  [%s]  N=%d  ATE=%.4f  AUTOC=%.4f  p=%.4f  tau range=[%.3f, %.3f]\n",
                key, res$N, res$ATE, res$AUTOC, res$p, min(tau), max(tau)))
  } else {
    cat(sprintf("FAIL  [%s]\n", key)); cat(paste(flags, collapse = "\n"), "\n")
  }
  invisible(ok)
}

results_named <- list(
  full  = res_full,
  top10 = results_reduced$top10,
  top20 = results_reduced$top20,
  top30 = results_reduced$top30
)

all_pass <- TRUE
for (key in names(expected)) {
  ok <- check_model(key, results_named[[key]], expected[[key]])
  all_pass <- all_pass && ok
}

# AUTOC of the reduced models. The Top 10/20/30 AUTOCs are all ~0.20 and lie
# within one another's SEs (~0.05); their numeric rank order sits inside grf's
# Monte-Carlo noise and can vary by grf version.
autocs <- sapply(results_named, function(r) r$AUTOC)
best   <- names(which.max(autocs))
cat(sprintf("\nReduced-model AUTOCs: top10 = %.4f, top20 = %.4f, top30 = %.4f (numerically largest: %s).\n",
            autocs["top10"], autocs["top20"], autocs["top30"], best))
cat("  (Top 10/20/30 AUTOCs are within one another's SEs.)\n")

if (!all_pass) stop("Pipeline integrity check failed — review flags above before continuing.")
cat("\nAll checks passed. Proceeding with subgroup analysis.\n")
```

------------------------------------------------------------------------

## Benefit Subgroups — Top-20 Model

### Subgroup Assignment

```{r subgroup-assign}
tau_df_20 <- results_reduced$top20$tau_df

q20_cut <- quantile(tau_df_20$tau, 0.20)
q80_cut <- quantile(tau_df_20$tau, 0.80)

cat(sprintf("CATE cutpoints:  20th pct = %.4f  |  80th pct = %.4f\n", q20_cut, q80_cut))

tau_df_20 <- tau_df_20 %>%
  mutate(
    benefit_group = case_when(
      tau <  q20_cut ~ "Non-Responders",
      tau >= q80_cut ~ "High Responders",
      TRUE           ~ "Moderate Responders"
    ),
    benefit_group = factor(
      benefit_group,
      levels  = c("Non-Responders", "Moderate Responders", "High Responders"),
      ordered = TRUE
    )
  )

group_summary <- tau_df_20 %>%
  group_by(benefit_group) %>%
  summarise(N = n(), mean_CATE = round(mean(tau), 4), sd_CATE = round(sd(tau), 4),
            min_CATE = round(min(tau), 4), max_CATE = round(max(tau), 4), .groups = "drop")

knitr::kable(group_summary,
  col.names = c("Group", "N", "Mean CATE", "SD", "Min CATE", "Max CATE"))
```

### Descriptive Table + Heatmap + Profile Table

```{r subgroup-table}
top20_ordered <- c(
  "t1_promis_eddep04", "t1_promis_eddep22", "t1_promis_eddep29", "t1_promis_eddep06",
  "t1_pss10_8", "t1_pss10_5", "t1_pss10_2", "t1_pss10_6",
  "t1_globalass9", "t1_globalass19", "t1_globalass18",
  "t1_meaninglife3", "t1_meaninglife4", "t1_meaninglife1",
  "t1_burnout10", "t1_burnout11", "t1_burnout9",
  "t1_hmi_4", "t1_hmi_1",
  "t1_compassion5"
)
stopifnot(setequal(top20_ordered, top20_cols))

label_map <- tribble(
  ~variable,              ~scale,                          ~item_label,
  "t1_promis_eddep04", "PROMIS Depression",              "I felt worthless",
  "t1_promis_eddep22", "PROMIS Depression",              "I felt like a failure",
  "t1_promis_eddep29", "PROMIS Depression",              "I felt depressed",
  "t1_promis_eddep06", "PROMIS Depression",              "I felt helpless",
  "t1_pss10_8",        "PSS-10 (Self-efficacy)†",   "Things were going my way",
  "t1_pss10_5",        "PSS-10 (Helplessness)",          "Upset because things were out of my control",
  "t1_pss10_2",        "PSS-10 (Helplessness)",          "Unable to control important things in life",
  "t1_pss10_6",        "PSS-10 (Helplessness)",          "Difficulties piling up too high to overcome",
  "t1_globalass9",     "GACS-24 (Character Strengths)",  "Vitality",
  "t1_globalass19",    "GACS-24 (Character Strengths)",  "Self-regulation",
  "t1_globalass18",    "GACS-24 (Character Strengths)",  "Prudence",
  "t1_meaninglife3",   "Meaning in Life",                "Good idea of what makes life meaningful",
  "t1_meaninglife4",   "Meaning in Life",                "Have discovered a meaningful life purpose",
  "t1_meaninglife1",   "Meaning in Life",                "Understand the meaning of my life",
  "t1_burnout10",      "MBI (Burnout)",                  "I feel frustrated by my work",
  "t1_burnout11",      "MBI (Burnout)",                  "I feel I am working too hard at my job",
  "t1_burnout9",       "MBI (Burnout)",                  "I feel full of energy",
  "t1_hmi_4",          "Healthy Minds Index",            "I notice when thoughts lead to other thoughts",
  "t1_hmi_1",          "Healthy Minds Index",            "When I want to focus, it is easy for me",
  "t1_compassion5",    "Compassion (CEA)",               "I tolerate feelings that are part of others' distress"
) %>%
  mutate(variable = factor(variable, levels = top20_ordered))

analysis_data <- full_data %>%
  select(id, all_of(top20_ordered)) %>%
  inner_join(tau_df_20 %>% select(id, benefit_group), by = "id")

stopifnot(nrow(analysis_data) == nrow(tau_df_20))

desc_long <- analysis_data %>%
  pivot_longer(cols = all_of(top20_ordered), names_to = "variable", values_to = "value") %>%
  group_by(variable, benefit_group) %>%
  summarise(mean_val = mean(value, na.rm = TRUE), sd_val = sd(value, na.rm = TRUE), .groups = "drop") %>%
  mutate(cell = sprintf("%.2f (%.2f)", mean_val, sd_val)) %>%
  select(variable, benefit_group, cell) %>%
  pivot_wider(names_from = benefit_group, values_from = cell)

desc_table <- label_map %>%
  mutate(variable = as.character(variable)) %>%
  left_join(desc_long %>% mutate(variable = as.character(variable)), by = "variable") %>%
  arrange(match(variable, top20_ordered)) %>%
  select(scale, item_label, `Non-Responders`, `Moderate Responders`, `High Responders`)

knitr::kable(desc_table,
  col.names = c("Scale", "Item", "Non-Responders", "Moderate Responders", "High Responders"))
```

```{r subgroup-heatmap}
#| fig-width: 9
#| fig-height: 9

scale_order <- c(
  "PROMIS Depression", "PSS-10 (Helplessness)", "PSS-10 (Self-efficacy)†",
  "GACS-24 (Character Strengths)", "Meaning in Life", "MBI (Burnout)",
  "Healthy Minds Index", "Compassion (CEA)"
)

heat_data <- analysis_data %>%
  pivot_longer(cols = all_of(top20_ordered), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  mutate(z = (value - mean(value, na.rm = TRUE)) / sd(value, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(variable, benefit_group) %>%
  summarise(z_mean = mean(z, na.rm = TRUE), .groups = "drop") %>%
  left_join(label_map %>% mutate(variable = as.character(variable)), by = "variable") %>%
  mutate(
    scale = factor(scale, levels = scale_order),
    item_label = factor(item_label, levels = rev(label_map$item_label)),
    benefit_group = factor(benefit_group,
                           levels = c("Non-Responders", "Moderate Responders", "High Responders"))
  )

# ── Profile table: VI + subgroup z-scores ──────────────────────────────────
vi_20 <- results_reduced$top20$vi_df %>%
  filter(variable %in% top20_ordered) %>%
  select(variable, importance)

z_wide <- heat_data %>%
  select(variable, benefit_group, z_mean) %>%
  pivot_wider(names_from = benefit_group, values_from = z_mean)

label_map_merged <- label_map %>%
  mutate(variable = as.character(variable),
         scale    = if_else(str_detect(scale, "PSS-10"), "PSS-10", scale))

# Ordered by descending summed scale VI so the profile table row order matches
# the descending-importance order used in the Results text (Depression 0.24 >
# GACS 0.20 > PSS-10 0.16 > MBI 0.13 > Meaning 0.11 > HMI 0.10 > Compassion 0.08).
scale_order_tbl <- c(
  "PROMIS Depression", "GACS-24 (Character Strengths)", "PSS-10", "MBI (Burnout)",
  "Meaning in Life", "Healthy Minds Index", "Compassion (CEA)"
)

item_data_tbl <- label_map_merged %>%
  left_join(vi_20 %>% mutate(variable = as.character(variable)), by = "variable") %>%
  left_join(z_wide %>% mutate(variable = as.character(variable)), by = "variable") %>%
  arrange(match(variable, top20_ordered))

tbl_rows <- list()
for (s in scale_order_tbl) {
  items     <- item_data_tbl %>% filter(scale == s)
  n_items   <- nrow(items)
  summed_vi <- sum(items$importance, na.rm = TRUE)
  mean_lo   <- mean(items$`Non-Responders`,      na.rm = TRUE)
  mean_mo   <- mean(items$`Moderate Responders`, na.rm = TRUE)
  mean_hi   <- mean(items$`High Responders`,     na.rm = TRUE)

  tbl_rows[[length(tbl_rows) + 1]] <- data.frame(
    Predictor            = paste0("**", s, " (", n_items, ")**"),
    VI                   = sprintf("%.2f", summed_vi),
    `Non-Responders`     = sprintf("%.2f", mean_lo),
    `Moderate Responders`= sprintf("%.2f", mean_mo),
    `High Responders`    = sprintf("%.2f", mean_hi),
    stringsAsFactors = FALSE, check.names = FALSE
  )
  # Item rows indented with non-breaking spaces (U+00A0) so the indent survives
  # read_csv(trim_ws = TRUE) and Word rendering (see Table 1 cat_block note).
  item_indent <- strrep(" ", 4)
  for (i in seq_len(nrow(items))) {
    tbl_rows[[length(tbl_rows) + 1]] <- data.frame(
      Predictor            = paste0(item_indent, items$item_label[i]),
      VI                   = sprintf("%.2f", items$importance[i]),
      `Non-Responders`     = sprintf("%.2f", items$`Non-Responders`[i]),
      `Moderate Responders`= sprintf("%.2f", items$`Moderate Responders`[i]),
      `High Responders`    = sprintf("%.2f", items$`High Responders`[i]),
      stringsAsFactors = FALSE, check.names = FALSE
    )
  }
}

profile_table_df <- do.call(rbind, tbl_rows)

cat("Profile table built:", nrow(profile_table_df), "rows.  VI sum check (should be 1.000):",
    round(sum(vi_20$importance), 3), "\n")

ggplot(heat_data, aes(x = benefit_group, y = item_label, fill = z_mean)) +
  geom_tile(colour = "white", linewidth = 0.4) +
  geom_text(aes(label = sprintf("%.2f", z_mean)), size = 3, colour = "black") +
  scale_fill_gradient2(low = "#2166ac", mid = "white", high = "#d6604d", midpoint = 0,
    limits = c(-1.5, 1.5), oob = scales::squish, name = "Within-variable\nz-score") +
  facet_grid(scale ~ ., scales = "free_y", space = "free_y",
             labeller = labeller(scale = label_wrap_gen(18))) +
  labs(x = NULL, y = NULL, title = "Baseline Predictor Profiles by Benefit Subgroup") +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 9),
        strip.text.y = element_text(angle = 0, hjust = 0, size = 8.5, face = "bold"),
        panel.grid = element_blank(), legend.position = "right")
```

## Top-20 Evaluation Forest (Re-fit for Subgroup ATE)

```{r refit-top20-eval-forest}
Y_raw_20 <- mydata$distress_factor * -1
keep_20  <- !is.na(Y_raw_20) & !is.na(ipw_composite) & ipw_composite > 0

X_20   <- as.matrix(mydata %>% select(all_of(top20_cols)))[keep_20, , drop = FALSE]
Y_20   <- as.numeric(scale(Y_raw_20[keep_20]))
W_20   <- W_all[keep_20]
wt_20  <- as.numeric(ipw_composite[keep_20])
pid_20 <- pid_all[keep_20]

stopifnot(
  nrow(X_20) == results_reduced$top20$N,
  identical(pid_20, results_reduced$top20$tau_df$id)
)

cat(sprintf("[%s] Fitting top-20 eval forest (seed = 1)...\n", format(Sys.time(), "%H:%M:%S")))
set.seed(1)
eval_forest_top20 <- causal_forest(X_20, Y_20, W_20,
  sample.weights = wt_20, num.trees = 4000, seed = 1, num.threads = 1L)

ate_check <- average_treatment_effect(eval_forest_top20)
cat(sprintf("Re-fit ATE = %.4f vs. cached ATE = %.4f — diff = %.4f\n",
            ate_check["estimate"], results_reduced$top20$ATE,
            abs(ate_check["estimate"] - results_reduced$top20$ATE)))
stopifnot(abs(ate_check["estimate"] - results_reduced$top20$ATE) < 0.001)
```

## Subgroup ATE Test — Top-20 Model

```{r subgroup-ate-test}
stopifnot(identical(tau_df_20$id, pid_20))

idx_low  <- which(tau_df_20$benefit_group == "Non-Responders")
idx_mod  <- which(tau_df_20$benefit_group == "Moderate Responders")
idx_high <- which(tau_df_20$benefit_group == "High Responders")

ate_low  <- average_treatment_effect(eval_forest_top20, subset = idx_low)
ate_mod  <- average_treatment_effect(eval_forest_top20, subset = idx_mod)
ate_high <- average_treatment_effect(eval_forest_top20, subset = idx_high)

diff_est <- as.numeric(ate_high["estimate"] - ate_low["estimate"])
diff_se  <- sqrt(as.numeric(ate_high["std.err"])^2 + as.numeric(ate_low["std.err"])^2)
diff_z   <- diff_est / diff_se
diff_p   <- 2 * pnorm(-abs(diff_z))

cat(sprintf("Subgroup ATEs (top-20):  Non = %.3f (SE %.3f)  Mod = %.3f (SE %.3f)  High = %.3f (SE %.3f)\n",
            ate_low["estimate"], ate_low["std.err"],
            ate_mod["estimate"], ate_mod["std.err"],
            ate_high["estimate"], ate_high["std.err"]))
cat(sprintf("High vs. Non-responder contrast:  diff = %.3f  (SE = %.3f)  z = %.2f  p = %.4g\n",
            diff_est, diff_se, diff_z, diff_p))
```

## Severity Benchmark — Heterogeneity Beyond Baseline Distress (Top-20)

```{r severity-benchmark}
# --- Regenerate t1_composite (baseline distress) from the 31 baseline items. ---
# Mirrors efa_change_scores.qmd Part 1 exactly: sorted PROMIS items, then PSS-10
# and WHO-5; unrotated 1-factor ML EFA on the polychoric correlation with
# regression scores; t1 factor score standardized to its own mean/SD.
anx_items_t1  <- sort(names(full_data)[grepl("^t1_promis_edanx", names(full_data))])
dep_items_t1  <- sort(names(full_data)[grepl("^t1_promis_eddep", names(full_data))])
pss_items_t1  <- paste0("t1_pss10_", 1:10)
who5_items_t1 <- paste0("t1_who5_",  1:5)
all_items_t1  <- c(anx_items_t1, dep_items_t1, pss_items_t1, who5_items_t1)

t1_mat_comp        <- as.data.frame(full_data[, all_items_t1])
t1_item_means_comp <- colMeans(t1_mat_comp, na.rm = TRUE)
t1_item_sds_comp   <- apply(t1_mat_comp, 2, sd, na.rm = TRUE)
poly_comp          <- psych::polychoric(t1_mat_comp)
n_obs_comp         <- sum(complete.cases(t1_mat_comp))

efa_comp <- psych::fa(r = poly_comp$rho, nfactors = 1, n.obs = n_obs_comp,
                      rotate = "none", fm = "ml", scores = "regression")

# t1 factor score (regression weights on baseline-standardized items).
t1_std_items <- sweep(sweep(as.matrix(t1_mat_comp), 2, t1_item_means_comp, "-"),
                      2, t1_item_sds_comp, "/")
t1_score <- as.vector(t1_std_items %*% efa_comp$weights)
t1_score[!complete.cases(t1_mat_comp)] <- NA
t1_composite_vec <- (t1_score - mean(t1_score, na.rm = TRUE)) / sd(t1_score, na.rm = TRUE)

sev_efa <- data.frame(id = full_data$id, t1_composite = t1_composite_vec)

sev_df <- tau_df_20 %>%
  left_join(sev_efa %>% select(id, t1_composite), by = "id")
stopifnot(identical(sev_df$id, pid_20))        # row order matches the eval forest

# A few baseline values are missing -> median-impute so the priority vector is complete.
t1c   <- sev_df$t1_composite
t1c[is.na(t1c)] <- median(t1c, na.rm = TRUE)

# Shared AUTOC settings — identical to the primary call in run_hte().
autoc_rule <- function(pri) {
  set.seed(12345)
  ro <- rank_average_treatment_effect(eval_forest_top20, priorities = pri,
          target = "AUTOC", q = seq(0.05, 1, length.out = 100), R = 200)
  c(est = as.numeric(ro$estimate), se = as.numeric(ro$std.err),
    p   = 2 * pnorm(-abs(ro$estimate / ro$std.err)))
}

# Integrity guard: scoring the forest CATE here must reproduce the primary top-20 AUTOC.
a_forest <- autoc_rule(sev_df$tau)
cat(sprintf("Forest-CATE AUTOC (guard) = %.4f  vs. cached %.4f\n",
            a_forest["est"], results_reduced$top20$AUTOC))
stopifnot(abs(a_forest["est"] - results_reduced$top20$AUTOC) < 0.001)

# Severity-only rule, and the residualized rule (CATE | baseline distress removed).
a_sevonly <- autoc_rule(t1c)
a_resid   <- autoc_rule(residuals(lm(sev_df$tau ~ t1c)))

cat(sprintf("Severity-only AUTOC (baseline distress as priority)   = %.4f  (SE %.4f)  p = %.4g\n",
            a_sevonly["est"], a_sevonly["se"], a_sevonly["p"]))
cat(sprintf("Residual AUTOC (CATE | baseline distress removed)     = %.4f  (SE %.4f)  p = %.4g\n",
            a_resid["est"], a_resid["se"], a_resid["p"]))
```

------------------------------------------------------------------------

# Part B — Component Models (4 Component Outcomes)

## Component Full Models

The four component full models (used for the 5-outcome ATE/AUTOC matrix
and for the per-component eval forests) are fit via `run_hte()` and held in
memory.

```{r component-config}
component_config <- list(
  list(key = "anxiety",    col = "t8.anx.scale",    label = "PROMIS Anxiety",    direction = "negate"),
  list(key = "depression", col = "t8.dep.scale",    label = "PROMIS Depression", direction = "negate"),
  list(key = "stress",     col = "t8.stress.scale", label = "PSS-10 Stress",     direction = "negate"),
  list(key = "wellbeing",  col = "t8_wellbeing",    label = "WHO-5 Wellbeing",   direction = "keep")
)
```

```{r component-full-run}
# Full component models held in memory (comp_full); consumed by the VI-extraction
# loop and the 5-outcome summary below.
comp_full <- list()
for (cfg in component_config) {
  cat(sprintf("[%s] Fitting component full model: %s\n", format(Sys.time(), "%H:%M:%S"), cfg$label))
  comp_full[[cfg$key]] <- run_hte(
    outcome_col = cfg$col, label = cfg$label, direction = cfg$direction,
    ipw_vec = ipw_weights[[cfg$key]], mydata = mydata,
    X_mat = X_all, W_all = W_all, pid_all = pid_all,
    p_cols = pred_cols, grp_map = group_map
  )
}
```

## Step 1: Extract Individual VI From Each Component Full Model

Eval-only refit (deterministic given `set.seed(1) + seed = 1`) to
extract individual VI for top-N selection and to save the per-component
eval forest for subgroup ATEs. Validates the eval-only ATE against the
cached main-analysis ATE.

```{r extract-vi-fn}
extract_eval_vi <- function(outcome_col, label, direction,
                             ipw_vec, mydata, X_mat, W_all, pid_all,
                             p_cols, grp_map, n_trees = 4000) {
  Y_raw <- mydata[[outcome_col]]
  if (direction == "negate") Y_raw <- Y_raw * -1

  keep <- !is.na(Y_raw) & !is.na(ipw_vec) & ipw_vec > 0
  X   <- X_mat[keep, , drop = FALSE]
  Y   <- as.numeric(scale(Y_raw[keep]))
  W   <- W_all[keep]
  wt  <- as.numeric(ipw_vec[keep])
  pid <- pid_all[keep]
  N   <- sum(keep)

  cat(sprintf("    N = %d  (W=1: %d, W=0: %d)  predictors = %d\n",
              N, sum(W == 1), sum(W == 0), ncol(X)))

  set.seed(1)
  eval_forest <- causal_forest(X, Y, W, sample.weights = wt, num.trees = n_trees, seed = 1, num.threads = 1L)

  ate_obj <- average_treatment_effect(eval_forest)
  ATE     <- as.numeric(ate_obj["estimate"]); ATE_SE <- as.numeric(ate_obj["std.err"])

  vi_raw <- variable_importance(eval_forest)
  vi_df  <- data.frame(variable = p_cols, importance = as.numeric(vi_raw)) %>%
    left_join(grp_map %>% select(variable, group), by = "variable") %>%
    mutate(group = tidyr::replace_na(group, "Other / unmapped")) %>%
    arrange(desc(importance))

  list(label = label, outcome_col = outcome_col,
       N = N, N_treated = sum(W == 1), N_control = sum(W == 0),
       ATE = ATE, ATE_SE = ATE_SE, vi_df = vi_df, eval_forest = eval_forest, pid = pid)
}
```

```{r extract-vi-loop}
vi_results        <- list()
full_cached       <- list()
comp_eval_forests <- list()   # in-memory per-component eval forests (for subgroup ATEs)

for (cfg in component_config) {
  key <- cfg$key
  cat(sprintf("\n----- %s -----\n", cfg$label))

  full_cached[[key]] <- comp_full[[key]]   # in-memory full main-analysis model

  cat(sprintf("[%s] Fitting eval forest (seed=1) to extract VI...\n", format(Sys.time(), "%H:%M:%S")))
  tmp <- extract_eval_vi(
    outcome_col = cfg$col, label = cfg$label, direction = cfg$direction,
    ipw_vec = ipw_weights[[key]], mydata = mydata, X_mat = X_all,
    W_all = W_all, pid_all = pid_all, p_cols = pred_cols, grp_map = group_map
  )
  vi_results[[key]]        <- tmp[setdiff(names(tmp), c("eval_forest", "pid"))]
  comp_eval_forests[[key]] <- list(forest = tmp$eval_forest, pid = tmp$pid)

  r_new <- vi_results[[key]]; r_old <- full_cached[[key]]; tol <- 1e-4
  ate_diff <- abs(r_new$ATE - r_old$ATE); ate_se_diff <- abs(r_new$ATE_SE - r_old$ATE_SE)
  n_diff <- r_new$N - r_old$N

  if (ate_diff > tol || ate_se_diff > tol || n_diff != 0) {
    cat(sprintf("  WARNING: ATE / N mismatch vs cached main-analysis result\n"))
    stop(sprintf("ATE reproducibility check failed for '%s'.", key))
  } else {
    cat(sprintf("  PASS  ATE = %.4f (SE = %.4f)  matches cached main-analysis.\n",
                r_new$ATE, r_new$ATE_SE))
  }
}

cat("\nAll VI extractions complete and validated.\n")
```

## Step 2: Fit Top 10 / 20 / 30 Reduced Models for Each Component

```{r run-reduced-models}
all_results_comp <- list()

for (cfg in component_config) {
  key <- cfg$key
  cat(sprintf("\n==========  %s  ==========\n", cfg$label))

  vi_all_c   <- vi_results[[key]]$vi_df
  reduced_configs_c <- list(
    list(n = 10, cols = vi_all_c$variable[1:10]),
    list(n = 20, cols = vi_all_c$variable[1:20]),
    list(n = 30, cols = vi_all_c$variable[1:30])
  )

  results_reduced_c <- list()

  for (rc in reduced_configs_c) {
    key_r   <- sprintf("top%d", rc$n)
    label_r <- sprintf("%s — Top %d Predictors", cfg$label, rc$n)

    cat(sprintf("[%s] Fitting: %s\n", format(Sys.time(), "%H:%M:%S"), label_r))
    X_sub   <- as.matrix(mydata %>% select(all_of(rc$cols)))
    grp_sub <- group_map %>% filter(variable %in% rc$cols)
    results_reduced_c[[key_r]] <- run_hte(
      outcome_col = cfg$col, label = label_r, direction = cfg$direction,
      ipw_vec = ipw_weights[[key]], mydata = mydata,
      X_mat = X_sub, W_all = W_all, pid_all = pid_all,
      p_cols = rc$cols, grp_map = grp_sub
    )
  }

  all_results_comp[[key]] <- list(
    full  = full_cached[[key]],
    top10 = results_reduced_c$top10,
    top20 = results_reduced_c$top20,
    top30 = results_reduced_c$top30
  )
}

cat("\nAll component reduced models complete.\n")
```

## Combined 5-Outcome Summary (Composite + Components)

```{r summary-combined}
sig_mark <- function(p) dplyr::case_when(p < .001 ~ "***", p < .01 ~ "**", p < .05 ~ "*", TRUE ~ "")

canonical_label <- setNames(
  sapply(component_config, function(x) x$label),
  sapply(component_config, function(x) x$key)
)
n_pred_full <- length(pred_cols)

# Long-form component rows
rows <- list()
for (key in names(all_results_comp)) {
  for (sub in c("full", "top10", "top20", "top30")) {
    r      <- all_results_comp[[key]][[sub]]
    n_pred <- if (sub == "full") n_pred_full else r$n_predictors
    rows[[length(rows) + 1]] <- tibble(
      outcome = canonical_label[[key]], key = key, config = sub,
      N = r$N, n_pred = n_pred,
      ATE = r$ATE, ATE_SE = r$ATE_SE, AUTOC = r$AUTOC, AUTOC_SE = r$AUTOC_SE, p = r$p
    )
  }
}
long_df <- bind_rows(rows)

# Composite rows (in-memory objects from Part A)
comp_rows <- list(
  list(r = res_full,                sub = "full"),
  list(r = results_reduced$top10,   sub = "top10"),
  list(r = results_reduced$top20,   sub = "top20"),
  list(r = results_reduced$top30,   sub = "top30")
)
comp_df <- bind_rows(lapply(comp_rows, function(x) {
  tibble(outcome = "Distress Composite", key = "composite", config = x$sub,
         N = x$r$N, n_pred = x$r$n_predictors,
         ATE = x$r$ATE, ATE_SE = x$r$ATE_SE,
         AUTOC = x$r$AUTOC, AUTOC_SE = x$r$AUTOC_SE, p = x$r$p)
}))

combined_df <- bind_rows(comp_df, long_df %>% select(names(comp_df))) %>%
  mutate(outcome = factor(outcome,
    levels = c("Distress Composite", "WHO-5 Wellbeing", "PROMIS Anxiety",
               "PROMIS Depression", "PSS-10 Stress"))) %>%
  arrange(outcome, match(config, c("full", "top10", "top20", "top30")))

# Benjamini-Hochberg FDR within each outcome across the three reduced specs
# (Top 10/20/30, one family per outcome). The Full (184-predictor) model is the
# no-selection baseline and keeps its raw p. p_star drives the significance stars
# in the AUTOC table (Table 3): raw p for Full, FDR-adjusted p for the reduced specs.
bh_reduced <- function(p, config) {
  out <- p                                    # Full keeps its raw p
  red <- config != "full"
  out[red] <- p.adjust(p[red], method = "BH")
  out
}
combined_df <- combined_df %>%
  group_by(outcome) %>%
  mutate(p_star = bh_reduced(p, config),
         p_BH   = ifelse(config == "full", NA_real_, p_star)) %>%
  ungroup()

# ATE matrix (outcome × config)
ate_mat <- combined_df %>%
  mutate(config = factor(config, levels = c("full", "top10", "top20", "top30"),
                         labels = c("Full", "Top 10", "Top 20", "Top 30")),
         ate_str = sprintf("%.3f (%.3f)%s", ATE, ATE_SE,
                           sig_mark(2 * pnorm(-abs(ATE / ATE_SE))))) %>%
  select(Outcome = outcome, N, config, ate_str) %>%
  pivot_wider(names_from = config, values_from = ate_str)

# AUTOC matrix (outcome × config). Each predictor specification is emitted as a PAIR of
# columns — the AU-TOC estimate (carrying the significance stars) and a separate SE column
# (bare number, no parentheses) — per Ron's "Est (SE) pairs" request. Stars use p_star: raw p
# for Full, FDR-adjusted p (BH within outcome across the three reduced specs) for Top 10/20/30.
# See note in the manuscript Table 2 caption.
autoc_mat <- combined_df %>%
  mutate(config = factor(config, levels = c("full", "top10", "top20", "top30"),
                         labels = c("Full", "Top 10", "Top 20", "Top 30")),
         est = sprintf("%.3f%s", AUTOC, sig_mark(p_star)),
         se  = sprintf("%.3f", AUTOC_SE)) %>%
  select(Outcome = outcome, N, config, est, se) %>%
  pivot_wider(names_from = config, values_from = c(est, se),
              names_glue = "{config}__{.value}") %>%
  select(Outcome, N,
         `Full`         = `Full__est`,    `Full SE`   = `Full__se`,
         `Top 10`       = `Top 10__est`,  `Top 10 SE` = `Top 10__se`,
         `Top 20`       = `Top 20__est`,  `Top 20 SE` = `Top 20__se`,
         `Top 30`       = `Top 30__est`,  `Top 30 SE` = `Top 30__se`)

knitr::kable(ate_mat,   caption = "Table 2 — ATE (SE) across 5 outcomes × predictor subsets.")
knitr::kable(autoc_mat, caption = "Table 3 — AUTOC (SE) across 5 outcomes × predictor subsets.")
```

## AUTOC FDR Correction Across Reduced Specs (Exploratory)

```{r autoc-fdr}
fdr_df <- combined_df %>%
  filter(config %in% c("top10", "top20", "top30")) %>%
  mutate(config  = factor(config, levels = c("top10", "top20", "top30"),
                          labels = c("Top 10", "Top 20", "Top 30")),
         sig_raw = sig_mark(p),
         sig_BH  = sig_mark(p_BH)) %>%
  arrange(outcome, config) %>%
  select(Outcome = outcome, Spec = config, AUTOC, AUTOC_SE,
         p_raw = p, sig_raw, p_BH, sig_BH)

knitr::kable(fdr_df, digits = 4,
  caption = "AUTOC with Benjamini-Hochberg FDR correction across the three reduced specs (Top 10/20/30), applied separately within each outcome.")
```

## Variable Importance Distribution Figure (eFigure)

```{r vi-scree}
vi_panels <- list(
  tibble(outcome = "Distress Composite", vi = res_full$vi_df$importance),
  tibble(outcome = "WHO-5 Wellbeing",   vi = vi_results$wellbeing$vi_df$importance),
  tibble(outcome = "PROMIS Anxiety",    vi = vi_results$anxiety$vi_df$importance),
  tibble(outcome = "PROMIS Depression", vi = vi_results$depression$vi_df$importance),
  tibble(outcome = "PSS-10 Stress",     vi = vi_results$stress$vi_df$importance)
)

vi_scree_df <- bind_rows(lapply(vi_panels, function(d) {
  d %>% arrange(desc(vi)) %>% mutate(rank = row_number())
})) %>%
  mutate(outcome = factor(outcome,
    levels = c("Distress Composite", "WHO-5 Wellbeing", "PROMIS Anxiety",
               "PROMIS Depression", "PSS-10 Stress")))

p_vi_scree <- ggplot(vi_scree_df, aes(x = rank, y = vi)) +
  geom_vline(xintercept = c(10, 20, 30), colour = "grey70", linetype = "dashed", linewidth = 0.3) +
  geom_line(colour = "#01665e", linewidth = 0.6) +
  geom_point(colour = "#01665e", size = 0.9) +
  facet_wrap(~ outcome, ncol = 2, scales = "free_y") +
  labs(x = "Predictor rank (by split-frequency importance)",
       y = "Split-frequency importance",
       title = "Variable importance distribution across full models",
       subtitle = "Dashed lines = ranks 10, 20, 30") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))

print(p_vi_scree)
```

------------------------------------------------------------------------

# Part C — Engagement Analyses

## Load engagement data

```{r eng-load-verify}
# Engagement metrics (week-13 sessions attended and app minutes) are PRE-MERGED
# into the de-identified file. They live on `full_data` (the untouched copy taken
# at read-in); `mydata` was rebuilt into the predictor matrix above and no longer
# carries them. Arm is joined from `mydata` so the coding is identical to the one
# the forests used. The public file carries no exp_group column, so the treatment
# arm is taken from `intervention_group` (control = 0; engagement is
# structurally zero in control).
df_eng <- full_data %>%
  dplyr::select(id, week_13_total_attendance, week_13_app_minutes) %>%
  dplyr::left_join(mydata %>% dplyr::select(id, intervention_group), by = "id") %>%
  dplyr::select(id, intervention_group, week_13_total_attendance, week_13_app_minutes)

stopifnot(nrow(df_eng) == nrow(mydata), !any(is.na(df_eng$intervention_group)))
df_eng$total_session_engagement <- df_eng$week_13_total_attendance
df_eng$total_app_minutes        <- df_eng$week_13_app_minutes

cat("df_eng rows:", nrow(df_eng), "\n")
cat("Intervention-arm rows (intervention_group == 1):",
    sum(df_eng$intervention_group == 1), "\n")
```

## Full-sample CATE assignment (extend top-20 CATEs to non-completers)

Re-fits the 10 top-20 fold causal forests with identical seeds
(sanity-checked to reproduce the cached OOF CATEs exactly), then assigns
each non-completer a CATE = mean of the 10 held-out fold forests, so
engagement can be compared across the full intervention arm.

```{r refit-top20-fold-forests}
Y_raw_t20 <- mydata$distress_factor * -1
keep_t20  <- !is.na(Y_raw_t20) & !is.na(ipw_composite) & ipw_composite > 0

X_t20   <- as.matrix(mydata %>% select(all_of(top20_cols)))[keep_t20, , drop = FALSE]
Y_t20   <- as.numeric(scale(Y_raw_t20[keep_t20]))
W_t20   <- W_all[keep_t20]
wt_t20  <- as.numeric(ipw_composite[keep_t20])
pid_t20 <- pid_all[keep_t20]
N_t20   <- sum(keep_t20)

stopifnot(N_t20 == results_reduced$top20$N,
          identical(pid_t20, results_reduced$top20$tau_df$id))

K <- 10
foldID_t20 <- integer(N_t20)
set.seed(12345)
for (g in 0:1) {
  idx <- which(W_t20 == g)
  foldID_t20[idx] <- sample(rep(1:K, length.out = length(idx)))
}

cat(sprintf("[%s] Fitting 10 top-20 fold forests...\n", format(Sys.time(), "%H:%M:%S")))
fold_forests_t20 <- vector("list", K)
for (fold in 1:K) {
  train <- which(foldID_t20 != fold)
  set.seed(123456 + fold)
  fold_forests_t20[[fold]] <- causal_forest(
    X_t20[train, , drop = FALSE], Y_t20[train], W_t20[train],
    sample.weights = wt_t20[train], num.trees = 4000, seed = 123456 + fold, num.threads = 1L)
  cat(sprintf("  fold %2d/%d done\n", fold, K))
}
```

```{r refit-oof-sanity}
tau_oof_refit <- rep(NA_real_, N_t20)
for (fold in 1:K) {
  test <- which(foldID_t20 == fold)
  tau_oof_refit[test] <- as.numeric(predict(fold_forests_t20[[fold]],
                                            X_t20[test, , drop = FALSE])$predictions)
}
stopifnot(sum(is.na(tau_oof_refit)) == 0)
diff_max <- max(abs(tau_oof_refit - results_reduced$top20$tau_df$tau))
cat(sprintf("Refit vs. cached OOF tau:  max |diff| = %.2e\n", diff_max))
stopifnot(diff_max < 1e-10)
cat("Sanity check passed — fold forests reproduce cached OOF CATEs exactly.\n")
```

```{r noncompleter-cates}
nc_idx <- which(!keep_t20)
N_nc   <- length(nc_idx)
X_nc   <- as.matrix(mydata[nc_idx, top20_cols, drop = FALSE])
pid_nc <- pid_all[nc_idx]
stopifnot(sum(is.na(X_nc)) == 0)

nc_preds <- matrix(NA_real_, nrow = N_nc, ncol = K)
for (fold in 1:K) {
  nc_preds[, fold] <- as.numeric(predict(fold_forests_t20[[fold]], X_nc)$predictions)
}
tau_nc <- rowMeans(nc_preds)
cat(sprintf("Non-completer N: %d  (completer N: %d  ;  total: %d)\n", N_nc, N_t20, N_nc + N_t20))
```

```{r tau-df-full}
tau_df_full <- bind_rows(
  results_reduced$top20$tau_df %>% mutate(completer = TRUE,  source = "OOF (held-out fold)"),
  tibble(id = pid_nc, tau = tau_nc) %>% mutate(completer = FALSE, source = "Mean of 10 fold forests")
)
stopifnot(nrow(tau_df_full) == nrow(mydata), !any(duplicated(tau_df_full$id)))

tau_df_full <- tau_df_full %>%
  mutate(
    benefit_group = case_when(
      tau <  q20_cut ~ "Non-Responders",
      tau >= q80_cut ~ "High Responders",
      TRUE           ~ "Moderate Responders"
    ),
    benefit_group = factor(benefit_group,
      levels = c("Non-Responders", "Moderate Responders", "High Responders"), ordered = TRUE)
  )
cat(sprintf("tau_df_full assembled:  N = %d  (completers = %d, non-completers = %d)\n",
            nrow(tau_df_full), sum(tau_df_full$completer), sum(!tau_df_full$completer)))
```

## Engagement by benefit subgroup (full intervention arm)

```{r eng-fullsample-merge}
int_eng <- df_eng[df_eng$intervention_group == 1, , drop = FALSE]
int_eng$id_chr <- as.character(int_eng$id)

sub_full_df <- tau_df_full %>%
  mutate(id_chr = as.character(id)) %>%
  select(id_chr, benefit_group, completer, tau)

ipw_df <- tibble(id_chr = as.character(mydata$id), ipw = ipw_composite)

merged_full <- int_eng %>%
  inner_join(sub_full_df, by = "id_chr") %>%
  left_join(ipw_df, by = "id_chr")

merged_full$benefit_group <- factor(merged_full$benefit_group,
  levels = c("Non-Responders", "Moderate Responders", "High Responders"))

cat(sprintf("Intervention participants matched to a subgroup: %d (completers = %d, non-completers = %d)\n",
            nrow(merged_full), sum(merged_full$completer), sum(!merged_full$completer)))
```

## Predicted-engagement interaction (does engageability moderate the ITT effect?)

Two 10-fold cross-validated regression forests predict each
participant's engagement from the full baseline predictor set; predicted
engagement is then tested as a moderator in an IPW-weighted linear model
with HC3 robust SEs.

```{r eng-interact-audit}
eng_for_merge <- df_eng %>%
  mutate(id_chr = as.character(id)) %>%
  select(id_chr, total_session_engagement, total_app_minutes)
mydata_id_chr <- as.character(mydata$id)
eng_lookup <- eng_for_merge[match(mydata_id_chr, eng_for_merge$id_chr), , drop = FALSE]
stopifnot(identical(eng_lookup$id_chr, mydata_id_chr))

eng_sess_all <- eng_lookup$total_session_engagement
eng_app_all  <- eng_lookup$total_app_minutes
```

```{r eng-interact-training-sets}
train_mask_sess <- (W_all == 1) & !is.na(eng_sess_all)
train_mask_app  <- (W_all == 1) & !is.na(eng_app_all)
N_train_sess <- sum(train_mask_sess)
N_train_app  <- sum(train_mask_app)
cat(sprintf("Training N — sessions RF: %d  |  app-min RF: %d\n", N_train_sess, N_train_app))
```

```{r eng-rf-sess-fit}
X_tr_sess <- X_all[train_mask_sess, , drop = FALSE]
Y_tr_sess <- as.numeric(eng_sess_all[train_mask_sess])
K <- 10
set.seed(12346)
foldID_sess <- sample(rep(1:K, length.out = N_train_sess))

cat(sprintf("[%s] Fitting 10 sessions-RF fold forests...\n", format(Sys.time(), "%H:%M:%S")))
fold_forests_sess <- vector("list", K)
for (fold in 1:K) {
  train <- which(foldID_sess != fold)
  set.seed(234567 + fold)
  fold_forests_sess[[fold]] <- regression_forest(
    X_tr_sess[train, , drop = FALSE], Y_tr_sess[train], num.trees = 4000, seed = 234567 + fold, num.threads = 1L)
  cat(sprintf("  sessions fold %2d/%d done\n", fold, K))
}
```

```{r eng-rf-sess-predict}
pred_sess <- rep(NA_real_, nrow(mydata))
for (fold in 1:K) {
  test_in_train <- which(foldID_sess == fold)
  train_rows    <- which(train_mask_sess)[test_in_train]
  pred_sess[train_rows] <- as.numeric(predict(fold_forests_sess[[fold]],
                                              X_all[train_rows, , drop = FALSE])$predictions)
}
nontr_rows <- which(!train_mask_sess)
if (length(nontr_rows) > 0) {
  nt_mat <- matrix(NA_real_, nrow = length(nontr_rows), ncol = K)
  for (fold in 1:K) {
    nt_mat[, fold] <- as.numeric(predict(fold_forests_sess[[fold]],
                                         X_all[nontr_rows, , drop = FALSE])$predictions)
  }
  pred_sess[nontr_rows] <- rowMeans(nt_mat)
}
stopifnot(sum(is.na(pred_sess)) == 0)
r2_sess <- 1 - sum((Y_tr_sess - pred_sess[train_mask_sess])^2) / sum((Y_tr_sess - mean(Y_tr_sess))^2)
cat(sprintf("Sessions RF — CV R^2 (n = %d): %.3f\n", N_train_sess, r2_sess))
```

```{r eng-rf-app-fit}
X_tr_app <- X_all[train_mask_app, , drop = FALSE]
Y_tr_app <- as.numeric(eng_app_all[train_mask_app])
set.seed(12347)
foldID_app <- sample(rep(1:K, length.out = N_train_app))

cat(sprintf("[%s] Fitting 10 app-min RF fold forests...\n", format(Sys.time(), "%H:%M:%S")))
fold_forests_app <- vector("list", K)
for (fold in 1:K) {
  train <- which(foldID_app != fold)
  set.seed(345678 + fold)
  fold_forests_app[[fold]] <- regression_forest(
    X_tr_app[train, , drop = FALSE], Y_tr_app[train], num.trees = 4000, seed = 345678 + fold, num.threads = 1L)
  cat(sprintf("  app-min  fold %2d/%d done\n", fold, K))
}
```

```{r eng-rf-app-predict}
pred_app <- rep(NA_real_, nrow(mydata))
for (fold in 1:K) {
  test_in_train <- which(foldID_app == fold)
  train_rows    <- which(train_mask_app)[test_in_train]
  pred_app[train_rows] <- as.numeric(predict(fold_forests_app[[fold]],
                                             X_all[train_rows, , drop = FALSE])$predictions)
}
nontr_rows <- which(!train_mask_app)
if (length(nontr_rows) > 0) {
  nt_mat <- matrix(NA_real_, nrow = length(nontr_rows), ncol = K)
  for (fold in 1:K) {
    nt_mat[, fold] <- as.numeric(predict(fold_forests_app[[fold]],
                                         X_all[nontr_rows, , drop = FALSE])$predictions)
  }
  pred_app[nontr_rows] <- rowMeans(nt_mat)
}
stopifnot(sum(is.na(pred_app)) == 0)
r2_app <- 1 - sum((Y_tr_app - pred_app[train_mask_app])^2) / sum((Y_tr_app - mean(Y_tr_app))^2)
cat(sprintf("App-min RF — CV R^2 (n = %d): %.3f\n", N_train_app, r2_app))
```

```{r eng-pred-frame}
# Per-participant predicted engagement (used in the interaction table note correlation).
pred_eng_df <- tibble(
  id        = pid_all,
  W         = W_all,
  arm       = if_else(W_all == 1, "Intervention", "Control"),
  pred_sess = pred_sess,
  pred_app  = pred_app
)
```

```{r eng-interact-frame}
ia_df <- mydata %>%
  mutate(id_chr = as.character(id)) %>%
  select(id_chr, distress_factor, intervention_group) %>%
  mutate(
    ipw   = ipw_composite,
    Zsess = as.numeric(scale(pred_sess)),
    Zapp  = as.numeric(scale(pred_app)),
    T     = intervention_group
  )
keep_ia <- !is.na(ia_df$distress_factor) & !is.na(ia_df$ipw) & ia_df$ipw > 0
ia_df   <- ia_df[keep_ia, , drop = FALSE]
cat(sprintf("Interaction analysis N (composite observed, ipw > 0): %d\n", nrow(ia_df)))
```

```{r eng-interact-fits}
fit_sess <- lm(distress_factor ~ T * Zsess, data = ia_df, weights = ipw)
fit_app  <- lm(distress_factor ~ T * Zapp,  data = ia_df, weights = ipw)

if (requireNamespace("sandwich", quietly = TRUE) && requireNamespace("lmtest", quietly = TRUE)) {
  cat("\n--- Sessions × T (HC3) ---\n")
  print(lmtest::coeftest(fit_sess, vcov. = sandwich::vcovHC(fit_sess, type = "HC3")))
  cat("\n--- App minutes × T (HC3) ---\n")
  print(lmtest::coeftest(fit_app,  vcov. = sandwich::vcovHC(fit_app,  type = "HC3")))
}
```

------------------------------------------------------------------------

# Part D — Paper Tables and Figures

## Table 1 — Baseline characteristics by treatment arm

```{r tab1-demographics}
# Table 1. Baseline Characteristics of Participants by Treatment Arm. Note. Values are M (SD)
#   for continuous characteristics and No. (%) for categorical characteristics; percentages are
#   within-arm and may not sum to 100 because of missing data or rounding. Low-frequency health
#   professions are collapsed into "Other" to match the analytic predictor coding. All data were
#   collected at the baseline (preintervention) assessment, before randomization. The two arms are
#   balanced by design (block randomization stratified by state and facility type).
# Built from the raw read (full_data); descriptive only — adds no analytic result.

df1 <- full_data %>%
  mutate(.arm = ifelse(group == "intervention", "Intervention", "Control"))
n_int <- sum(df1$.arm == "Intervention")
n_ctl <- sum(df1$.arm == "Control")

fmt_msd <- function(x, arm) {
  v <- x[df1$.arm == arm]; sprintf("%.1f (%.1f)", mean(v, na.rm = TRUE), sd(v, na.rm = TRUE))
}
fmt_np <- function(flag, arm) {
  v <- flag[df1$.arm == arm]; sprintf("%d (%.1f)", sum(v, na.rm = TRUE), 100 * mean(v, na.rm = TRUE))
}
row_cont <- function(label, x)
  data.frame(Characteristic = label, Intervention = fmt_msd(x, "Intervention"),
             Control = fmt_msd(x, "Control"), check.names = FALSE)
row_cat <- function(label, flag)
  data.frame(Characteristic = label, Intervention = fmt_np(flag, "Intervention"),
             Control = fmt_np(flag, "Control"), check.names = FALSE)
hdr <- function(label)
  data.frame(Characteristic = label, Intervention = "", Control = "", check.names = FALSE)
cat_block <- function(header, fct) {
  # Indent category levels with non-breaking spaces (U+00A0): regular spaces are
  # stripped by read_csv(trim_ws = TRUE) in the manuscript and collapsed by Word,
  # so they do not survive to the rendered table. nbsp renders as literal indent.
  indent <- "    "
  rows <- lapply(levels(fct), function(lv) row_cat(paste0(indent, lv), fct == lv & !is.na(fct)))
  do.call(rbind, c(list(hdr(header)), rows))
}

# Sex
g <- tolower(trimws(as.character(df1$gender)))
sex_cat <- factor(dplyr::case_when(
  g %in% c("female", "mujer", "femenino", "f") ~ "Female",
  g %in% c("male", "hombre", "masculino", "m") ~ "Male",
  TRUE ~ "Preferred not to answer"),
  levels = c("Female", "Male", "Preferred not to answer"))

# Profession (collapsed to the 9-category analytic coding)
prof <- as.character(factor(df1$profession, levels = 1:15,
  labels = c("Physicians", "Nurses", "Optometry", "Dentistry", "Biomedical sciences",
             "Psychology", "Health promotion", "Social work", "Chemistry",
             "Radiology technician", "Laboratory technician", "Physical therapy",
             "Nutrition", "Public health", "Other")))
prof[prof %in% c("Optometry", "Biomedical sciences", "Health promotion",
                 "Radiology technician", "Laboratory technician", "Public health")] <- "Other"
prof <- factor(prof, levels = c("Physicians", "Nurses", "Dentistry", "Psychology",
                                "Social work", "Chemistry", "Physical therapy",
                                "Nutrition", "Other"))

# Educational attainment and marital status
ed <- factor(suppressWarnings(as.integer(df1$ed_level_reduced)), levels = c(2, 3, 4, 5, 6, 7),
  labels = c("Secondary", "Technical career", "Bachelor's degree",
             "Graduate: specialty", "Graduate: master's", "Graduate: doctorate"))
mstat <- factor(suppressWarnings(as.integer(df1$marital_status)), levels = 1:5,
  labels = c("Single", "Married", "Cohabiting", "Separated", "Widowed"))

tab1_demographics <- do.call(rbind, list(
  row_cont("Age, y, M (SD)", df1$age),
  cat_block("Sex, No. (%)", sex_cat),
  row_cont("Years working in health care, M (SD)", df1$yrs_work),
  cat_block("Profession, No. (%)", prof),
  cat_block("Educational attainment, No. (%)", ed),
  cat_block("Marital status, No. (%)", mstat)
))
names(tab1_demographics) <- c("Characteristic",
  sprintf("Intervention (n = %d)", n_int), sprintf("Control (n = %d)", n_ctl))

cat("Table 1 built (Intervention n =", n_int, "| Control n =", n_ctl, ")\n")
print(tab1_demographics, row.names = FALSE)
```

------------------------------------------------------------------------

## Figure 1 — Observed ATE by predicted-CATE quintile (top-20 model)

```{r fig1-quintile}
# Figure 1. Observed ATE Within Quintiles of Predicted CATE (Top-20 Model).
# Note. ATE = doubly-robust AIPW estimate within each quintile bin of the predicted CATE from
# the top-20 model. Units are SDs of the EFA composite distress score (higher = greater
# benefit). Error bars are 95% CIs. The monotonically increasing gradient confirms that the
# CATE ranking successfully orders participants by observed benefit.
tau20 <- results_reduced$top20$tau_df$tau
stopifnot(length(tau20) == length(eval_forest_top20$Y.hat))

qbreaks <- quantile(tau20, probs = seq(0, 1, length.out = 6), na.rm = TRUE)
qbin    <- cut(tau20, breaks = qbreaks, labels = 1:5, include.lowest = TRUE)

quint_df <- lapply(1:5, function(q) {
  idx <- which(qbin == q)
  a   <- average_treatment_effect(eval_forest_top20, subset = idx)
  tibble(quintile = q, N = length(idx), predicted = mean(tau20[idx]),
         observed = as.numeric(a["estimate"]), se = as.numeric(a["std.err"]))
}) %>% bind_rows()

p_fig1 <- ggplot(quint_df, aes(x = factor(quintile), y = observed)) +
  geom_hline(yintercept = 0, linetype = "dotted", colour = "grey60") +
  geom_col(fill = "#01665e", alpha = 0.85, width = 0.65) +
  geom_errorbar(aes(ymin = observed - 1.96 * se, ymax = observed + 1.96 * se),
                width = 0.18, colour = "grey25") +
  labs(x = "Predicted-CATE quintile (1 = lowest predicted benefit)",
       y = "Observed ATE (AIPW, within quintile)") +
  theme_minimal(base_size = 10)

print(p_fig1)
```

## Table 2 — ATE matrix / Table 3 — AUTOC matrix

```{r export-tab2-tab3}
# Table 2. Doubly-Robust Average Treatment Effects (ATEs) Across Outcomes and Predictor
#   Specifications. Note. Values are ATE (SE) in SD units of each outcome (distress outcomes
#   sign-reversed so positive = benefit). Full = all 184 predictors; Top 10/20/30 = reduced
#   forests re-fit on predictors ranked by split-frequency variable importance.
# Table 3. AUTOC Statistics Across Outcomes and Predictor Specifications. Note. Values are
#   AUTOC (SE). * p < .05. ** p < .01. *** p < .001. All tests two-sided.
print(ate_mat); print(autoc_mat)
```

## Table 4 — Subgroup ATEs across all five outcomes

```{r export-tab4-subgroup}
# Table 4. Doubly-Robust ATEs (SE) Within Predicted-Benefit Subgroups for All Five Outcomes.
#   Note. Subgroups defined by composite top-20 CATE percentiles: Non-responders = bottom 20%
#   (n = n_lo), Moderate = middle 60% (n = n_mo), High = top 20% (n = n_hi). Values are Est, SE
#   in SD units of each outcome; distress outcomes sign-reversed so positive = benefit. Component
#   Ns may differ slightly due to outcome-specific attrition. EFA Composite High-vs-Non-responder contrast:
#   Δ, SE, z, p (see below).
pid20 <- results_reduced$top20$tau_df$id
benefit_group <- tau_df_20$benefit_group

comp_keys <- list(
  list(key = "wellbeing",  label = "WHO-5 Wellbeing"),
  list(key = "anxiety",    label = "PROMIS Anxiety"),
  list(key = "depression", label = "PROMIS Depression"),
  list(key = "stress",     label = "PSS-10 Stress")
)
comp_ef <- lapply(comp_keys, function(cfg) comp_eval_forests[[cfg$key]])
names(comp_ef) <- sapply(comp_keys, function(x) x$key)

sg_lookup <- data.frame(id = pid20, sg = as.character(benefit_group), stringsAsFactors = FALSE)

subgroup_cell <- function(ef, idx) {
  a   <- average_treatment_effect(ef, subset = idx)
  est <- as.numeric(a["estimate"]); se <- as.numeric(a["std.err"])
  p   <- 2 * pnorm(-abs(est / se))   # Wald test of the subgroup ATE against zero
  star <- ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", "")))
  # Estimate (with stars) and SE as separate strings; SE carries no parentheses so it can
  # occupy its own column (Ron's "Est (SE) pairs" request).
  c(est = sprintf("%.3f%s", est, star), se = sprintf("%.3f", se))
}

# Build one table row as Outcome + (Est, SE) pairs for the three subgroups.
subgroup_row <- function(label, nr, mo, hi) {
  data.frame(
    Outcome                  = label,
    `Non-Responders`         = nr["est"], `Non-Responders SE`      = nr["se"],
    `Moderate Responders`    = mo["est"], `Moderate Responders SE` = mo["se"],
    `High Responders`        = hi["est"], `High Responders SE`     = hi["se"],
    check.names = FALSE, stringsAsFactors = FALSE, row.names = NULL
  )
}

composite_row <- subgroup_row(
  "Distress Composite",
  subgroup_cell(eval_forest_top20, idx_low),
  subgroup_cell(eval_forest_top20, idx_mod),
  subgroup_cell(eval_forest_top20, idx_high)
)

comp_rows_tbl <- lapply(comp_keys, function(cfg) {
  ef    <- comp_ef[[cfg$key]]$forest
  pid_c <- comp_ef[[cfg$key]]$pid
  matched_sg <- sg_lookup$sg[match(pid_c, sg_lookup$id)]
  subgroup_row(
    cfg$label,
    subgroup_cell(ef, which(matched_sg == "Non-Responders")),
    subgroup_cell(ef, which(matched_sg == "Moderate Responders")),
    subgroup_cell(ef, which(matched_sg == "High Responders"))
  )
})

combined_sg <- bind_rows(composite_row, bind_rows(comp_rows_tbl))

n_lo <- length(idx_low); n_mo <- length(idx_mod); n_hi <- length(idx_high)
cat(sprintf("Table 3 note inputs — subgroup Ns: Non-responders = %d, Moderate = %d, High = %d\n",
            n_lo, n_mo, n_hi))
cat(sprintf("Distress Composite High-vs-Non-responder (Results text, not the note): diff = %.3f (SE = %.3f), z = %.2f, p = %.4g\n",
            diff_est, diff_se, diff_z, diff_p))

print(combined_sg)
```

## Table 5 — Top-20 VI profile by subgroup

```{r export-tab5-profile}
# Table 5. Baseline Predictor Profiles by Benefit Subgroup (Top-20 Model). Note. Bold rows are
#   scale-level summaries: VI is the sum across items; z-score columns show the mean
#   within-variable z-score across items. Item rows show individual VI and within-variable
#   z-scores. VI is from the top-20 model and sums to 1.00 across all 20 items. Z-scores are
#   standardized to the overall completer mean and SD (N = 1,435). PSS-10 item 8 is a
#   self-efficacy item (higher = less stress; reverse of the three helplessness items).
#   Columns: Predictor | VI | Non-Responders | Moderate Responders | High Responders.
print(profile_table_df)
```

## Table 6 — Engagement by predicted-benefit subgroup

```{r export-tab6-eng-subgroup}
# Table 6 (eTable 3). Intervention Engagement by Predicted-Benefit Subgroup (Full Intervention
#   Arm). Note text (computed live below): n, KW chi-square + p for sessions and app minutes,
#   High-vs-Non-responder Holm-adjusted Wilcoxon p, and the right-skew/ANOVA caveat.
eng_desc <- merged_full %>%
  group_by(benefit_group) %>%
  summarise(
    N = n(),
    sess_mean = mean(total_session_engagement, na.rm = TRUE),
    sess_sd   = sd(total_session_engagement,   na.rm = TRUE),
    sess_median = median(total_session_engagement, na.rm = TRUE),
    sess_iqr  = IQR(total_session_engagement,  na.rm = TRUE),
    app_mean  = mean(total_app_minutes, na.rm = TRUE),
    app_sd    = sd(total_app_minutes,   na.rm = TRUE),
    app_median = median(total_app_minutes, na.rm = TRUE),
    app_iqr   = IQR(total_app_minutes,  na.rm = TRUE),
    .groups = "drop"
  )

eng_subgroup_df <- data.frame(
  Subgroup             = as.character(eng_desc$benefit_group),
  N                    = eng_desc$N,
  `Sessions, M (SD)`      = sprintf("%.2f (%.2f)", eng_desc$sess_mean, eng_desc$sess_sd),
  `Median Sessions (IQR)` = sprintf("%.0f (%.0f)", eng_desc$sess_median, eng_desc$sess_iqr),
  `App min, M (SD)`       = sprintf("%.2f (%.2f)", eng_desc$app_mean, eng_desc$app_sd),
  `App min, Mdn (IQR)` = sprintf("%.1f (%.1f)", eng_desc$app_median, eng_desc$app_iqr),
  check.names = FALSE, stringsAsFactors = FALSE
)

# Live test statistics for the manuscript note.
kw_sess <- kruskal.test(total_session_engagement ~ benefit_group, data = merged_full)
kw_app  <- kruskal.test(total_app_minutes        ~ benefit_group, data = merged_full)
pw_sess <- pairwise.wilcox.test(merged_full$total_session_engagement,
                                merged_full$benefit_group, p.adjust.method = "holm")$p.value
pw_app  <- pairwise.wilcox.test(merged_full$total_app_minutes,
                                merged_full$benefit_group, p.adjust.method = "holm")$p.value
aov_app_p <- summary(aov(total_app_minutes ~ benefit_group, data = merged_full))[[1]]["benefit_group", "Pr(>F)"]
fmt_p_note <- function(p) ifelse(p < .001, "< .001", sprintf("= %.3f", p))
cat(sprintf(paste0("Note inputs — n = %d; sessions KW chi2(2) = %.2f, p %s, High-vs-Non %s; ",
                   "app KW chi2(2) = %.2f, p %s, High-vs-Non %s; app ANOVA p = %.2f\n"),
            nrow(merged_full),
            unname(kw_sess$statistic), fmt_p_note(kw_sess$p.value),
            fmt_p_note(pw_sess["High Responders", "Non-Responders"]),
            unname(kw_app$statistic),  fmt_p_note(kw_app$p.value),
            fmt_p_note(pw_app["High Responders", "Non-Responders"]),
            aov_app_p))

# The omnibus Kruskal-Wallis test (chi-square/p, above) is reported in the manuscript Table A4
# *Note.*; the pairwise High-vs-Non-responder differences are reported in the Results text. So
# the exported CSV stays purely descriptive (no significance rows) — ZJ's call to de-clutter.

print(eng_subgroup_df)
```

## Table 7 — Predicted-engagement interaction

```{r export-tab7-eng-interaction}
# Table 7 (eTable 4). Predicted-Engagement Moderation of the Treatment Effect on Distress.
#   Note. IPW-weighted linear models (distress ~ T + Zhat + T x Zhat) with HC3 robust SEs;
#   n = nrow(ia_df). Entries are b (SE). Distress is the EFA composite in its RAW (non-reversed)
#   metric, so a negative coefficient = lower distress (benefit). Zhat = standardized predicted
#   engagement from a 10-fold CV regression forest (CV R^2 shown). Predicted engagement
#   correlated r (sessions) / r (app minutes) with the top-20 CATE. * p<.05 ** p<.01 *** p<.001.
hc3_coef <- function(fit) {
  if (requireNamespace("sandwich", quietly = TRUE) && requireNamespace("lmtest", quietly = TRUE)) {
    as.data.frame(unclass(lmtest::coeftest(fit, vcov. = sandwich::vcovHC(fit, type = "HC3"))))
  } else as.data.frame(summary(fit)$coefficients)
}
ct_s <- hc3_coef(fit_sess); ct_a <- hc3_coef(fit_app)
star <- function(p) ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", "")))
cell <- function(ct, term) sprintf("%.2f (%.2f)%s", ct[term, 1], ct[term, 2], star(ct[term, 4]))

ce <- pred_eng_df %>%
  mutate(id_chr = as.character(id)) %>%
  inner_join(tau_df_full %>% mutate(id_chr = as.character(id)) %>% select(id_chr, tau), by = "id_chr")
r_sess_tau <- cor(ce$pred_sess, ce$tau)
r_app_tau  <- cor(ce$pred_app,  ce$tau)

eng_ia_df <- data.frame(
  `Predicted engagement`              = c("Sessions attended", "App minutes"),
  `Treatment assignment, b (SE)`      = c(cell(ct_s, "T"),       cell(ct_a, "T")),
  `Pred. engagement, b (SE)`          = c(cell(ct_s, "Zsess"),   cell(ct_a, "Zapp")),
  `Treatment × Pred. engagement, b (SE)` = c(cell(ct_s, "T:Zsess"), cell(ct_a, "T:Zapp")),
  `p (interaction)`                   = c(sprintf("%.3f", ct_s["T:Zsess", 4]), sprintf("%.3f", ct_a["T:Zapp", 4])),
  check.names = FALSE, stringsAsFactors = FALSE
)
# CV R2 dropped from the table body (tangential to the focal interaction test);
# its values are reported in the table note instead — see note inputs below.

cat(sprintf("Note inputs — n = %d; r(pred_sess, tau) = %.2f; r(pred_app, tau) = %.2f; CV R2: sessions = %.2f, app = %.2f\n",
            nrow(ia_df), r_sess_tau, r_app_tau, r2_sess, r2_app))

print(eng_ia_df)
```

## eTable 1 — Baseline predictor definitions

```{r export-etable1-predictors}
# eTable 1. Baseline Predictor Definitions. Note. Candidate baseline (preintervention)
#   predictors entered into the full causal forest (total_pred predictors). Continuous
#   predictors comprise individual item responses + demographic/SES indicators (scale totals
#   not entered separately, to avoid collinearity). Categorical predictors are dummy-coded.
#   Counts computed directly from the predictor matrix. Columns: Set | Items | Definition/
#   response format | Variable level.  >>> VERIFY instrument names + response anchors. <<<
pred_defs <- tibble::tribble(
  ~group,                                     ~domain,                        ~measure,                                                            ~ptype,       ~description,
  "WHO-5 items (t1)",                         "Mental health and well-being", "WHO-5 Well-Being Index",                                            "Continuous", "Past-2-week subjective well-being; each item rated 0 (at no time) to 5 (all of the time).",
  "PROMIS Anxiety items (t1)",                "Mental health and well-being", "PROMIS Adult Anxiety short form",                                   "Continuous", "Past-7-day anxiety symptoms; each item rated 1 (never) to 5 (always).",
  "PROMIS Depression items (t1)",             "Mental health and well-being", "PROMIS Adult Depression short form",                                "Continuous", "Past-7-day depressive symptoms; each item rated 1 (never) to 5 (always).",
  "PSS-10 items (t1)",                        "Mental health and well-being", "Perceived Stress Scale (PSS-10)",                                   "Continuous", "Past-month perceived stress; each item rated 0 (never) to 4 (very often).",
  "MBI / Burnout items (t1)",                 "Mental health and well-being", "Maslach Burnout Inventory",                                         "Continuous", "Emotional exhaustion and personal accomplishment items; each rated 0 (never) to 6 (every day).",
  "HMI items (t1)",                           "Well-being skills",            "Healthy Minds Index",                                               "Continuous", "Self-reported well-being skills across awareness, connection, insight, and purpose.",
  "MAIA items (t1)",                          "Well-being skills",            "Multidimensional Assessment of Interoceptive Awareness",            "Continuous", "Body awareness and interoceptive self-regulation; each item rated 0 to 5.",
  "FFMQ Awareness items (t1)",                "Well-being skills",            "Five Facet Mindfulness Questionnaire: Acting with Awareness",       "Continuous", "Attending to present-moment activity; each item rated 1 to 5.",
  "FFMQ Nonreact items (t1)",                 "Well-being skills",            "Five Facet Mindfulness Questionnaire: Nonreactivity",               "Continuous", "Nonreactivity to inner experience; each item rated 1 to 5.",
  "CERQ Reappraisal items (t1)",              "Well-being skills",            "Cognitive Emotion Regulation Questionnaire: Positive Reappraisal",  "Continuous", "Reappraisal-based emotion regulation; each item rated 1 to 5.",
  "IRI EC items (t1)",                        "Well-being skills",            "Interpersonal Reactivity Index: Empathic Concern",                  "Continuous", "Other-oriented feelings of sympathy and concern; each item rated 1 to 5.",
  "Compassion items (t1)",                    "Well-being skills",            "Compassion scale",                                                  "Continuous", "Dispositional compassion toward others.",
  "Meaning in Life items (t1)",               "Well-being skills",            "Meaning in Life Questionnaire",                                     "Continuous", "Presence of meaning in life; each item rated 1 to 7.",
  "Gratitude items (t1)",                     "Well-being skills",            "Gratitude Questionnaire-6 (GQ-6)",                                  "Continuous", "Dispositional gratitude; each item rated 1 to 7.",
  "Character strengths / GACS-24 items (t1)", "Well-being skills",            "Global Assessment of Character Strengths (GACS-24)",                "Continuous", "Self-rated character strengths.",
  "Demographics / SES",                       "Demographic and occupational", "Demographic and socioeconomic indicators",                          "Continuous", "Age, years working in health care, and household composition (people, rooms, bathrooms, internet access, vehicles).",
  "Gender",                                   "Demographic and occupational", "Gender",                                                            "Categorical",  "Male versus not male.",
  "State (dummy)",                            "Demographic and occupational", "State of residence",                                                "Categorical",  "Mexican state (one indicator per state).",
  "Profession (dummy)",                       "Demographic and occupational", "Health profession",                                                 "Categorical",  "Profession category (e.g., medicine, nursing, psychology).",
  "Job position (dummy)",                     "Demographic and occupational", "Job position",                                                      "Categorical",  "Occupational role category.",
  "Education (dummy)",                         "Demographic and occupational", "Education level",                                                   "Categorical",  "Highest completed education level.",
  "Marital status (dummy)",                   "Demographic and occupational", "Marital status",                                                    "Categorical",  "Marital status category.",
  "Training / clinical history",              "Demographic and occupational", "Prior training history",                                            "Continuous & categorical", "Prior socioemotional/contemplative training (yes/no) and cumulative training hours."
)

counts <- group_map %>% dplyr::count(group, name = "n_pred")
etable1_df <- pred_defs %>% dplyr::left_join(counts, by = "group")

missing_def <- setdiff(unique(group_map$group), pred_defs$group)
if (length(missing_def) > 0) stop("group_map groups with no definition row: ", paste(missing_def, collapse = ", "))
if (any(is.na(etable1_df$n_pred))) warning("Definition rows with no matching predictors.")
total_pred <- sum(etable1_df$n_pred, na.rm = TRUE)
stopifnot(total_pred == length(pred_cols))
if (total_pred != 184L) warning(sprintf("Predictor total is %d, not 184.", total_pred))
cat(sprintf("eTable 1 predictor total: %d (length(pred_cols) = %d).\n", total_pred, length(pred_cols)))

domain_levels <- c("Mental health and well-being", "Well-being skills", "Demographic and occupational")
etable1_display <- etable1_df %>%
  dplyr::mutate(domain = factor(domain, levels = domain_levels)) %>%
  dplyr::arrange(domain, dplyr::desc(n_pred)) %>%
  dplyr::transmute(
    Set                            = measure,
    Items                          = n_pred,
    `Definition / response format` = description,
    `Variable level`               = ptype
  )

print(etable1_display)
```

## eTable 2 — Outcome correlation matrix

```{r export-etable2-outcome-cors}
# eTable 2. Pairwise Correlations Among the Five 37-Week Outcomes. Note. Pairwise Pearson
#   correlations (pairwise-complete observations; N range n_min–n_max). Distress scales
#   correlate negatively with WHO-5 well-being and positively with one another. The EFA
#   Distress Composite is the single-factor score used as the primary CATE outcome.
#   * p<.05 ** p<.01 *** p<.001.
outcome_specs <- tibble::tribble(
  ~col,            ~label,
  "t8_wellbeing",  "WHO-5 Well-Being",
  "t8_anxiety",    "PROMIS Anxiety",
  "t8_depression", "PROMIS Depression",
  "t8_stress",     "PSS-10 Stress"
)
missing_cols <- setdiff(outcome_specs$col, names(full_data))
if (length(missing_cols) > 0) {
  stop("eTable 2: outcome columns not found in full_data: ", paste(missing_cols, collapse = ", "))
}

out_df <- full_data %>%
  dplyr::select(id, dplyr::all_of(outcome_specs$col)) %>%
  dplyr::left_join(distress_factor_raw %>% dplyr::select(id, distress_factor), by = "id")

cor_cols   <- c("distress_factor", outcome_specs$col)
cor_labels <- c("Distress Composite", outcome_specs$label)
M          <- as.matrix(out_df[, cor_cols]); colnames(M) <- cor_labels

cmat <- cor(M, use = "pairwise.complete.obs", method = "pearson")

k <- ncol(M); pmat <- matrix(NA_real_, k, k); nmat <- matrix(NA_integer_, k, k)
for (i in seq_len(k)) for (j in seq_len(k)) {
  if (i == j) next
  ok <- stats::complete.cases(M[, i], M[, j])
  nmat[i, j] <- sum(ok); pmat[i, j] <- stats::cor.test(M[ok, i], M[ok, j])$p.value
}
ns <- nmat[lower.tri(nmat)]; n_min <- min(ns); n_max <- max(ns)

star2 <- function(p) ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", ""))))
stars <- matrix(star2(pmat), k, k)

disp <- formatC(round(cmat, 2), format = "f", digits = 2)
disp <- sub("^(-?)0\\.", "\\1.", disp)
disp <- matrix(paste0(disp, as.vector(stars)), k, k)
disp[upper.tri(disp)] <- ""; diag(disp) <- "—"
cor_df <- data.frame(Outcome = cor_labels, disp, check.names = FALSE, stringsAsFactors = FALSE)
colnames(cor_df) <- c("Outcome", cor_labels); rownames(cor_df) <- NULL

cat(sprintf("eTable 2 pairwise-complete N range: %s–%s\n",
            format(n_min, big.mark = ","), format(n_max, big.mark = ",")))

print(cor_df)
```

## IPW diagnostics

```{r export-ipw-diagnostics}
# IPW response-model diagnostics for eMethods: per-arm cross-validated AUC (95% CI) and
# normalized-weight ranges among completers.
print(ipw_diagnostics)
```

------------------------------------------------------------------------

## Reproduction Complete

```{r repro-complete}
cat("All paper tables and figures reproduced inline above.\n")
cat("Pipeline integrity check (composite N / ATE / AUTOC / SE) passed earlier in the run.\n")
sessionInfo()
```
